---
title: "Beta diversity analysis"
author: "Rodolfo Pelinson"
date: "2026-03-31"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, warning=FALSE, echo = FALSE, include=FALSE}
dir<-("C:/Users/rodol/OneDrive/repos/PrioEff_TimeOfAssembly")
```

```{r}

source(paste(sep = "/",dir,"functions/null_assembly.R"))
source(paste(sep = "/",dir,"functions/null_com_algorithm.R"))
source(paste(sep = "/",dir,"functions/beta_deviation.R"))
source(paste(sep = "/",dir,"functions/beta_deviation.R"))
source(paste(sep = "/",dir,"functions/beta_deviation_siqueira_et_al_2019.R"))
source(paste(sep = "/",dir,"functions/letters.R"))
source(paste(sep = "/",dir,"functions/remove_sp.R"))


```

```{r, message = FALSE, warning = FALSE}
library(vegan)
library(glmmTMB)
library(car)
library(emmeans)
library(DHARMa)
library(yarrr)
library(vioplot)
```

```{r,  warning=FALSE, message = FALSE}
source(paste(sep = "/",dir,"ajeitando_planilhas.R"))
```

## Preparing data

Excluding the late treatment and preparing data
```{r}
comm_all_2 <- comm_all[Exp_design_all$treatments != "atrasado",]
Exp_design_all_2 <- Exp_design_all[Exp_design_all$treatments != "atrasado",]

comm_all_2 <- remove_sp(comm_all_2, 0)

ncol(comm_all_2)


nrow(comm_all_2)
nrow(Exp_design_all_2)


ID <-  as.factor(Exp_design_all_2$sites)

AM_by_block <- interaction(as.factor(Exp_design_all_2$block), as.factor( Exp_design_all_2$AM))


Exp_design_all_2$AM <- as.factor(Exp_design_all_2$AM)
Exp_design_all_2$AM_numeric <- as.numeric(Exp_design_all_2$AM)
Exp_design_all_2$AM_numeric_quad <- Exp_design_all_2$AM_numeric^2


Exp_design_all_2$AM_days <- Exp_design_all_2$AM_numeric
Exp_design_all_2$AM_days[Exp_design_all_2$AM_days == 1] <- 32
Exp_design_all_2$AM_days[Exp_design_all_2$AM_days == 2] <- 80
Exp_design_all_2$AM_days[Exp_design_all_2$AM_days == 3] <- 116
Exp_design_all_2$AM_days[Exp_design_all_2$AM_days == 4] <- 158


Exp_design_all_2$AM_days_orig <- Exp_design_all_2$AM_days

Exp_design_all_2$AM_days <- scale(Exp_design_all_2$AM_days)
attr_AM_days <- attributes(Exp_design_all_2$AM_days)

unscale <- function(x, atributes, reverse = FALSE){
  if(isTRUE(reverse)){
      x <- (x - atributes$`scaled:center`) / atributes$`scaled:scale` 
  }else{
      x <- (x * atributes$`scaled:scale`) + atributes$`scaled:center`
  }
  return(x)
}

Exp_design_all_2$AM_days <- Exp_design_all_2$AM_days[,1]
Exp_design_all_2$AM_days_quad <- Exp_design_all_2$AM_days^2

```


## Computing beta deviation

Running the beta deviation analysis keeps gamma diversity within each survey fixed, total number of individuals in each sample fixed, and average number of species in each survey fixed.

```{r, warning=FALSE}
beta_dev <-  beta_deviation(comm_all_2, keep_fill = TRUE, method = "quasiswap", dist = "bray", fixedmar="both", shuffle = "both", group = AM_by_block,
                                  strata = Exp_design_all_2$AM,  mtype = "count", times = 500, burnin = 0, thin = 1000, transform = NULL, seed = 1, type = "centroid", bias.adjust = FALSE)

```

```{r, echo=FALSE, eval=FALSE}
#Alternative ways to compute beta deviation
beta_dev <-  beta_deviation(comm_all_2, keep_fill = FALSE, method = "quasiswap", dist = "bray", fixedmar="both", shuffle = "both", group = AM_by_block,
                            strata = Exp_design_all_2$AM,  mtype = "count", times = 500, burnin = 0, thin = 1000, transform = NULL, seed = 1, type = "centroid", bias.adjust = FALSE)

```


```{r, echo=FALSE, eval=FALSE}
#Alternative ways to compute beta deviation
#Is equivalent to keeping fill = FALSE.
beta_dev <-  beta_deviation_siqueira_et_al_2019(comm_all_2, dist = "bray", group = AM_by_block,
                            keep.gamma = Exp_design_all_2$AM,  times = 500, transform = NULL, seed = 1)


```


```{r, echo=FALSE, eval=FALSE}
#Alternative ways to compute beta deviation

beta_dev <-  MY_beta_deviation(comm_all_2, dist = "bray", group = AM_by_block,
                                       strata = Exp_design_all_2$AM, times = 500, transform = NULL, seed = 1, type = "centroid", bias.adjust = FALSE)

```




## Checking premises

Checking if null matrices are keeping the parameters that should be fixed, fixed.

Gamma diversity
```{r}
gammas_AM1 <- rep(NA, length(beta_dev$null_cons))
for(i in 1:length(beta_dev$null_cons)){
  gammas_AM1[i] <- sum(decostand(colSums(beta_dev$null_cons[[i]][Exp_design_all_2$AM == 1,]), method = "pa"))
}
head(gammas_AM1)
tail(gammas_AM1)
#Original
sum(decostand(colSums(comm_all_2[Exp_design_all_2$AM == 1,]), method = "pa"))

#########################################################################################################################
gammas_AM2 <- rep(NA, length(beta_dev$null_cons))
for(i in 1:length(beta_dev$null_cons)){
  gammas_AM2[i] <- sum(decostand(colSums(beta_dev$null_cons[[i]][Exp_design_all_2$AM == 2,]), method = "pa"))
}
head(gammas_AM2)
tail(gammas_AM2)
sum(decostand(colSums(comm_all_2[Exp_design_all_2$AM == 2,]), method = "pa"))
#########################################################################################################################

gammas_AM3 <- rep(NA, length(beta_dev$null_cons))
for(i in 1:length(beta_dev$null_cons)){
  gammas_AM3[i] <- sum(decostand(colSums(beta_dev$null_cons[[i]][Exp_design_all_2$AM == 3,]), method = "pa"))
}
head(gammas_AM3)
tail(gammas_AM3)
sum(decostand(colSums(comm_all_2[Exp_design_all_2$AM == 3,]), method = "pa"))
#########################################################################################################################

gammas_AM4 <- rep(NA, length(beta_dev$null_cons))
for(i in 1:length(beta_dev$null_cons)){
  gammas_AM4[i] <- sum(decostand(colSums(beta_dev$null_cons[[i]][Exp_design_all_2$AM == 4,]), method = "pa"))
}
head(gammas_AM4)
tail(gammas_AM4)
sum(decostand(colSums(comm_all_2[Exp_design_all_2$AM == 4,]), method = "pa"))
#########################################################################################################################
```




Alpha diversity
```{r}
comalphas_AM1 <- list()
for(i in 1:length(beta_dev$null_cons)){
  comalphas_AM1[[i]]<- rowSums(decostand(beta_dev$null_cons[[i]][Exp_design_all_2$AM == 1,], method = "pa"))
}
head(comalphas_AM1)
tail(comalphas_AM1)
#Original
rowSums(decostand(comm_all_2[Exp_design_all_2$AM == 1,], method = "pa"))


alphas_AM1 <- rep(NA, length(beta_dev$null_cons))
for(i in 1:length(beta_dev$null_cons)){
  alphas_AM1[i] <- mean(rowSums(decostand(beta_dev$null_cons[[i]][Exp_design_all_2$AM == 1,], method = "pa")))
}
head(alphas_AM1)
tail(alphas_AM1)
#Original
mean(rowSums(decostand(comm_all_2[Exp_design_all_2$AM == 1,], method = "pa")))




#########################################################################################################################
alphas_AM2 <- rep(NA, length(beta_dev$null_cons))
for(i in 1:length(beta_dev$null_cons)){
  alphas_AM2[i] <- mean(rowSums(decostand(beta_dev$null_cons[[i]][Exp_design_all_2$AM == 2,], method = "pa")))
}
head(alphas_AM2)
tail(alphas_AM2)
#Original
mean(rowSums(decostand(comm_all_2[Exp_design_all_2$AM == 2,], method = "pa")))
#########################################################################################################################

alphas_AM3 <- rep(NA, length(beta_dev$null_cons))
for(i in 1:length(beta_dev$null_cons)){
  alphas_AM3[i] <- mean(rowSums(decostand(beta_dev$null_cons[[i]][Exp_design_all_2$AM == 3,], method = "pa")))
}
head(alphas_AM3)
tail(alphas_AM3)
#Original
mean(rowSums(decostand(comm_all_2[Exp_design_all_2$AM == 3,], method = "pa")))
#########################################################################################################################

alphas_AM4 <- rep(NA, length(beta_dev$null_cons))
for(i in 1:length(beta_dev$null_cons)){
  alphas_AM4[i] <- mean(rowSums(decostand(beta_dev$null_cons[[i]][Exp_design_all_2$AM == 4,], method = "pa")))
}
head(alphas_AM4)
tail(alphas_AM4)
#Original
mean(rowSums(decostand(comm_all_2[Exp_design_all_2$AM == 4,], method = "pa")))
#########################################################################################################################
```




Community sizes
```{r}
comsizes_AM1 <- list()
for(i in 1:length(beta_dev$null_cons)){
  comsizes_AM1[[i]]<- rowSums(beta_dev$null_cons[[i]][Exp_design_all_2$AM == 1,])
}
head(comsizes_AM1)
tail(comsizes_AM1)
#Original
rowSums(comm_all_2[Exp_design_all_2$AM == 1,])

#########################################################################################################################
comsizes_AM2 <- list()
for(i in 1:length(beta_dev$null_cons)){
  comsizes_AM2[[i]]<- rowSums(beta_dev$null_cons[[i]][Exp_design_all_2$AM == 2,])
}
head(comsizes_AM2)
tail(comsizes_AM2)
#Original
rowSums(comm_all_2[Exp_design_all_2$AM == 2,])
#########################################################################################################################
comsizes_AM3 <- list()
for(i in 1:length(beta_dev$null_cons)){
  comsizes_AM3[[i]]<- rowSums(beta_dev$null_cons[[i]][Exp_design_all_2$AM == 3,])
}
head(comsizes_AM3)
tail(comsizes_AM3)
#Original
rowSums(comm_all_2[Exp_design_all_2$AM == 3,])
#########################################################################################################################

comsizes_AM4 <- list()
for(i in 1:length(beta_dev$null_cons)){
  comsizes_AM4[[i]]<- rowSums(beta_dev$null_cons[[i]][Exp_design_all_2$AM == 4,])
}
head(comsizes_AM4)
tail(comsizes_AM4)
#Original
rowSums(comm_all_2[Exp_design_all_2$AM == 4,])
#########################################################################################################################
```


## Analysis


```{r,   fig.width = 6, fig.height = 3, dpi = 600, dev.args= list(pointsize=8)}
mod_obs_null <- glmmTMB(beta_dev$observed_distances ~ 1 + (1|block2/sites), data = Exp_design_all_2, control = glmmTMBControl(optimizer=optim, optArgs=list(method="BFGS")))
mod_exp_null <- glmmTMB(beta_dev$expected_distances ~ 1 + (1|block2/sites), data = Exp_design_all_2, control = glmmTMBControl(optimizer=optim, optArgs=list(method="BFGS")))
mod_dev_null <- glmmTMB(beta_dev$deviation_distances ~ 1 + (1|block2/sites), data = Exp_design_all_2, control = glmmTMBControl(optimizer=optim, optArgs=list(method="BFGS")))

mod_obs_am_num <- glmmTMB(beta_dev$observed_distances ~ AM_days + (1|block2/sites), data = Exp_design_all_2, control = glmmTMBControl(optimizer=optim, optArgs=list(method="BFGS")))
mod_exp_am_num <- glmmTMB(beta_dev$expected_distances ~ AM_days + (1|block2/sites), data = Exp_design_all_2, control = glmmTMBControl(optimizer=optim, optArgs=list(method="BFGS")))
mod_dev_am_num <- glmmTMB(beta_dev$deviation_distances ~ AM_days + (1|block2/sites), data = Exp_design_all_2, control = glmmTMBControl(optimizer=optim, optArgs=list(method="BFGS")))

mod_obs_am_num_quad <- glmmTMB(beta_dev$observed_distances ~ AM_days + AM_days_quad + (1|block2/sites), data = Exp_design_all_2, control = glmmTMBControl(optimizer=optim, optArgs=list(method="BFGS")))
mod_exp_am_num_quad <- glmmTMB(beta_dev$expected_distances ~ AM_days + AM_days_quad + (1|block2/sites), data = Exp_design_all_2, control = glmmTMBControl(optimizer=optim, optArgs=list(method="BFGS")))
mod_dev_am_num_quad <- glmmTMB(beta_dev$deviation_distances ~ AM_days + AM_days_quad + (1|block2/sites), data = Exp_design_all_2)

anova_obs <- anova(mod_obs_null, mod_obs_am_num, mod_obs_am_num_quad)
anova_obs
anova_exp <- anova(mod_exp_null, mod_exp_am_num, mod_exp_am_num_quad)
anova_exp
anova_dev <- anova(mod_dev_null, mod_dev_am_num, mod_dev_am_num_quad)
anova_dev

plot(simulateResiduals(mod_obs_am_num_quad))
plot(simulateResiduals(mod_exp_am_num_quad))
plot(simulateResiduals(mod_dev_am_num_quad))

```



## Making predictions
```{r}

new_data_days <- data.frame(AM_days = seq(from= min(Exp_design_all_2$AM_days), to = max(Exp_design_all_2$AM_days), length.out = 100),
                       AM_days_quad = seq(from= min(Exp_design_all_2$AM_days), to = max(Exp_design_all_2$AM_days), length.out = 100)^2)


predicted_obs <- predict(mod_obs_am_num, newdata = new_data_days, se.fit = TRUE, re.form = NA)
predicted_obs$upper <- predicted_obs$fit + predicted_obs$se.fit * qnorm(0.975)
predicted_obs$lower <- predicted_obs$fit + predicted_obs$se.fit * qnorm(0.025) 

predicted_exp_quad <- predict(mod_exp_am_num_quad, newdata = new_data_days, se.fit = TRUE, re.form = NA)
predicted_exp_quad$upper <- predicted_exp_quad$fit + predicted_exp_quad$se.fit * qnorm(0.975)
predicted_exp_quad$lower <- predicted_exp_quad$fit + predicted_exp_quad$se.fit * qnorm(0.025) 

predicted_dev <- predict(mod_dev_am_num, newdata = new_data_days, se.fit = TRUE, re.form = NA)
predicted_dev$upper <- predicted_dev$fit + predicted_dev$se.fit * qnorm(0.975)
predicted_dev$lower <- predicted_dev$fit + predicted_dev$se.fit * qnorm(0.025) 

```

## Plots
```{r,   fig.width = 6, fig.height = 3, dpi = 600, dev.args= list(pointsize=8)}
set.seed(1)
#svg(file = "plots/Community structure analysis/beta_deviation.svg", width = 6, height = 3, pointsize = 8)

par(mfrow = c(1,2))
#par(mar  = c(4,4,1,1), bty = "n")

unique_AM_days <- unique(Exp_design_all_2$AM_days)
unique_AM_days_orig <- unique(Exp_design_all_2$AM_days_orig)

#vioplot(beta_dev$observed_distances ~ AM_days, data = Exp_design_all_2, at = unique_AM_days,
#        h = 0.05, drawRect = FALSE, border = FALSE, side = "left",
#        xaxt = "n", yaxt = "n", ylab = "", xlab = "", ylim = c(0.1,0.8),
#        col = transparent("blue", trans.val = 0.85), wex = 20,  xlim = c(min(unique_AM_days)*1.1,max(unique_AM_days)*1.1), xaxs = "i")

#par(mar  = c(4,4,1,1), bty = "n", new = TRUE)
#vioplot(beta_dev$expected_distances ~ AM_days, data = Exp_design_all_2, at = unique_AM_days,
#        h = 0.005, drawRect = FALSE, border = FALSE, side = "right",
#        xaxt = "n", yaxt = "n", ylab = "", xlab = "", ylim = c(0.1,0.8),
#        col = transparent("red", trans.val = 0.85), wex = 20,  xlim = c(min(unique_AM_days)*1.1,max(unique_AM_days)*1.1), xaxs = "i")

par(mar  = c(4,4,1,1), bty = "l", new = FALSE)
plot(beta_dev$observed_distances ~ jitter(AM_days, 1),
     data = Exp_design_all_2, xaxt = "n", ylab = "", xlab = "", type = "n", ylim = c(0.1,0.8), xlim = c(min(unique_AM_days)*1.25,max(unique_AM_days)*1.25),  xaxs = "i")

polygon(x = c(new_data_days$AM_days[1:100], new_data_days$AM_days[100:1]),
        y = c(predicted_obs$upper[1:100], predicted_obs$lower[100:1]), col = transparent("blue", trans.val = 0.6), border = FALSE) 

polygon(x = c(new_data_days$AM_days[1:100], new_data_days$AM_days[100:1]),
        y = c(predicted_exp_quad$upper[1:100], predicted_exp_quad$lower[100:1]), col = transparent("red", trans.val = 0.6), border = FALSE) 


points(beta_dev$observed_distances ~ jitter(AM_days-0.075, 0.5), pch = 21, col= "black",bg = transparent("blue", trans.val = 0.75), cex = 1.1, data = Exp_design_all_2)
points(beta_dev$expected_distances ~ jitter(AM_days+0.075, 0.5), pch = 21, col= "black",bg = transparent("red", trans.val = 0.75), cex = 1.1, data = Exp_design_all_2)

lines(x = new_data_days$AM_days,y = predicted_obs$fit, col = "black", lwd = 2)
lines(x = new_data_days$AM_days,y = predicted_exp_quad$fit, col = "black", lwd = 2)


title(ylab = "Distance to centroid", cex.lab = 1.25, line= 2.25)
axis(1, at = unique_AM_days, labels = c("32", "80", "116", "158"))
title(xlab = "Days", cex.lab = 1.25 ,line = 2.25)

par(new = TRUE, mar = c(0,0,0,0), bty = "n")
plot(NA, ylim = c(0,100), xlim = c(0,100), xaxt = "n", yaxt = "n")

legend(legend = c("Observed",
                  "Expected"), x = 100, y = 18, bty = "n", pch = 21, col = "black", pt.bg = c(transparent("blue", trans.val = 0.75),transparent("red", trans.val = 0.75)), xjust = 1, yjust = 0)

letters(x = 5, y = 97, "a)", cex = 1.5)

#####################################################################################################################


#par(mar  = c(4,4,1,1), bty = "n")
#vioplot(MY_beta_dev$deviation_distances ~ AM_days, data = Exp_design_all_2, at = c(32,80,116,158),
#        h = 1, drawRect = FALSE, border = FALSE,
#        xaxt = "n", yaxt = "n", ylab = "", xlab = "", 
#        col = transparent("aquamarine2", trans.val = 0.8), wex = 20,  xlim = c(20,170), xaxs = "i")#, ylim = c(-3,5))

par(mar  = c(4,4,1,1), bty = "l", new = FALSE)
plot(beta_dev$deviation_distances ~ jitter(AM_days, 0.5),
     data = Exp_design_all_2, xaxt = "n", ylab = "", xlab = "", type = "n",  xlim = c(min(unique_AM_days)*1.25,max(unique_AM_days)*1.25), xaxs = "i")#, ylim = c(-3,5),)

polygon(x = c(new_data_days$AM_days[1:100], new_data_days$AM_days[100:1]),
        y = c(predicted_dev$upper[1:100], predicted_dev$lower[100:1]), col = transparent("grey50", trans.val = 0.5), border = FALSE) 

points(beta_dev$deviation_distances ~ jitter(AM_days, 1), pch = 21, col= "black",bg = transparent("aquamarine2", trans.val = 0.5), cex = 1.1, data = Exp_design_all_2)
lines(x = new_data_days$AM_days,y = predicted_dev$fit, col = "black", lwd = 2)
abline(h = 0, lwd = 1.5, lty = 2, col = "black")
title(ylab = "Deviation distances", cex.lab = 1.25, line= 2.25)
axis(1, at = unique_AM_days, labels = c("32", "80", "116", "158"))
title(xlab = "Days", cex.lab = 1.25 ,line = 2.25)

letters(x = 5, y = 97, "b)", cex = 1.5)


#dev.off()
```


Percentage increase in observed community variability:
```{r}
preds <- predict(mod_obs_am_num, newdata = data.frame(AM_days = c(unscale(32, attr_AM_days, TRUE),
                                                         unscale(158, attr_AM_days, TRUE))), se.fit = TRUE, re.form = NA)
((preds$fit[2] - preds$fit[1]) / preds$fit[1]) * 100
```

Peak of expected community variability:
```{r}
peak <- new_data_days$AM_days[which(predicted_exp_quad$fit %in% max(predicted_exp_quad$fit))]
unscale(peak, attr_AM_days, FALSE)
```

Percentage increase up to the peak of expected community variability :
```{r}
newdata <- data.frame(AM_days = c(unscale(32, attr_AM_days, TRUE), peak),
                      AM_days_quad = c(unscale(32, attr_AM_days, TRUE), peak)^2)
preds <- predict(mod_exp_am_num_quad, newdata = newdata, se.fit = TRUE, re.form = NA)
((preds$fit[2] - preds$fit[1]) / preds$fit[1]) * 100
```

Percentage decrease in expected community variability from the peak up to the end of the experiment:
```{r}
newdata <- data.frame(AM_days = c(peak, unscale(158, attr_AM_days, TRUE)),
                      AM_days_quad = c(peak, unscale(158, attr_AM_days, TRUE))^2)
preds <- predict(mod_exp_am_num_quad, newdata = newdata, se.fit = TRUE, re.form = NA)
((preds$fit[2] - preds$fit[1]) / preds$fit[1]) * 100
```


Percentage increase in deviation variability:
```{r}
preds <- predict(mod_dev_am_num, newdata = data.frame(AM_days = c(unscale(32, attr_AM_days, TRUE),
                                                         unscale(158, attr_AM_days, TRUE))), se.fit = TRUE, re.form = NA)

((preds$fit[2] - preds$fit[1]) / preds$fit[1]) * 100


```
