---
title: "Effect of first survey on the effect of time"
author: "Rodolfo Pelinson"
date: "`r Sys.Date()`"
output: 
  github_document: 
    fig_width: 10
    fig_height: 8
editor_options: 
  chunk_output_type: console
---

```{r, warning=FALSE, echo = FALSE, include=FALSE}
dir<-("C:/Users/rodol/OneDrive/repos/PrioEff_TimeOfAssembly")
```


## Loading packages and functions


```{r, warning=FALSE, message = FALSE}

source(paste(sep = "/",dir,"functions/pairwise_gllvm.R"))
source(paste(sep = "/",dir,"functions/pairwise_mvabund.R"))
source(paste(sep = "/",dir,"functions/my.anova.gllvm.R"))
source(paste(sep = "/",dir,"functions/My_coefplot.R"))
source(paste(sep = "/",dir,"functions/remove_sp.R"))
source(paste(sep = "/",dir,"functions/extract_mles.R"))
source(paste(sep = "/",dir,"functions/my_ordiplot.R"))
source(paste(sep = "/",dir,"functions/get_scaled_lvs.R"))
source(paste(sep = "/",dir,"functions/text_contour.R"))
source(paste(sep = "/",dir,"functions/letters.R"))

```

```{r, warning=FALSE, message = FALSE}

library(vegan)
library(gllvm)
library(mvabund)
library(DHARMa)
library(glmmTMB)
library(vioplot)
library(yarrr)
library(colorspace)

```


```{r}
sessionInfo()
```

## Loading and preparing data


```{r, message = FALSE, warning=FALSE}
source(paste(sep = "/",dir,"ajeitando_planilhas.R"))
```



```{r, message = FALSE, warning=FALSE}
comm_all_drop_atrasado <- comm_all[Exp_design_all$treatments != "atrasado",]
Exp_design_all_drop_atrasado <- Exp_design_all[Exp_design_all$treatments != "atrasado",]

ncol(comm_all_drop_atrasado)
comm_all_drop_atrasado_rm <- remove_sp(comm_all_drop_atrasado, 10)
ncol(comm_all_drop_atrasado_rm)

Exp_design_all_drop_atrasado$treatments_AM <- paste(Exp_design_all_drop_atrasado$treatments, Exp_design_all_drop_atrasado$AM, sep="_")

Exp_design_all_drop_atrasado$AM_numeric <- as.numeric(Exp_design_all_drop_atrasado$AM)

Exp_design_all_drop_atrasado$treatments <- as.factor(Exp_design_all_drop_atrasado$treatments)

AM_days <- as.numeric(Exp_design_all_drop_atrasado$AM)
AM_days[AM_days == 1] <- 32
AM_days[AM_days == 2] <- 80
AM_days[AM_days == 3] <- 116
AM_days[AM_days == 4] <- 158

AM_days_sc <- scale(AM_days)

Exp_design_all_drop_atrasado$AM_days_sc <- c(AM_days_sc)
Exp_design_all_drop_atrasado$AM_days_sc_squared <- c(AM_days_sc)^2

Exp_design_all_drop_atrasado$AM_days <- c(AM_days)
Exp_design_all_drop_atrasado$AM_days_squared <- c(AM_days)^2


comm_AM1 <- comm_all_drop_atrasado_rm[Exp_design_all_drop_atrasado$AM == 1,]
comm_AM1_rm <- remove_sp(comm_AM1, 3)



comm_AM1_pred <- rbind(comm_AM1_rm, comm_AM1_rm, comm_AM1_rm, comm_AM1_rm)

nrow(comm_AM1_pred)
nrow(Exp_design_all_drop_atrasado)
nrow(comm_all_drop_atrasado_rm)

comm_AM1_pred_st <- decostand(comm_AM1_pred, "stand")
colnames(comm_AM1_pred_st) <- gsub(" ", "_", colnames(comm_AM1_pred_st))

predictors <- data.frame(Exp_design_all_drop_atrasado, comm_AM1_pred_st)

```

## Using NMDS to describe initial communities.

```{r}

comm_AM1_rm_total <- data.frame(decostand(comm_AM1_rm, method = "total", MARGIN = 2))
nmds_comm_AM1_rm_total <- metaMDS(comm_AM1_rm_total, distance  = "bray", k = 2)
comm_AM1_nmds <- data.frame(nmds_comm_AM1_rm_total$points)
comm_AM1_nmds_st <- decostand(comm_AM1_nmds, method = "stand")

comm_AM1_nmds_st_pred <- rbind(comm_AM1_nmds_st, comm_AM1_nmds_st, comm_AM1_nmds_st, comm_AM1_nmds_st)

predictors_nmds <- data.frame(Exp_design_all_drop_atrasado, comm_AM1_nmds_st_pred)

```



### Testing for effects


```{r}

nrow(predictors_nmds)
nrow(comm_all_drop_atrasado_rm)

set.seed(1)
control <- permute::how(within = permute::Within(type = 'free'),
                        plots = Plots(strata = predictors_nmds$sites, type = 'free'),
                        nperm = 999)
permutations <- shuffleSet(nrow(comm_all_drop_atrasado_rm), control = control)


comm_all_drop_atrasado_mvabund <- mvabund(comm_all_drop_atrasado_rm)

mod_full_lin <- manyglm(comm_all_drop_atrasado_mvabund ~ block2 + ( MDS1 + MDS2 ) + AM_days_sc + AM_days_sc:( MDS1 + MDS2 ), family="negative.binomial",  data = predictors_nmds, composition = FALSE)

mod_full_quad <- manyglm(comm_all_drop_atrasado_mvabund ~ block2 + ( MDS1 + MDS2 ) + AM_days_sc + AM_days_sc_squared + AM_days_sc:( MDS1 + MDS2 ) + AM_days_sc_squared:( MDS1 + MDS2 ), family="negative.binomial",  data = predictors_nmds, composition = FALSE)

anova_quadratic_test <- anova(mod_full_lin, mod_full_quad, bootID = permutations, show.time = "all", cor.type = "I", test = "LR", resamp = "pit.trap")
anova_quadratic_test


########################################################
mod_block <- manyglm(comm_all_drop_atrasado_mvabund ~ block2 + ( MDS1 + MDS2 ) + AM_days_sc + AM_days_sc_squared, family="negative.binomial",  data = predictors_nmds, composition = FALSE)

mod_no_block <- manyglm(comm_all_drop_atrasado_mvabund ~ ( MDS1 + MDS2 ) + AM_days_sc + AM_days_sc_squared, family="negative.binomial",  data = predictors_nmds, composition = FALSE)

anova_block <- anova(mod_no_block, mod_block, bootID = permutations, show.block = "all", cor.type = "I", test = "LR", resamp = "pit.trap")
anova_block
########################################################


mod_time <- manyglm(comm_all_drop_atrasado_mvabund ~ block2 + ( MDS1 + MDS2 ) + AM_days_sc + AM_days_sc_squared, family="negative.binomial",  data = predictors_nmds, composition = FALSE)

mod_no_time <- manyglm(comm_all_drop_atrasado_mvabund ~ block2 + ( MDS1 + MDS2 ), family="negative.binomial",  data = predictors_nmds, composition = FALSE)

anova_time <- anova(mod_no_time, mod_time, bootID = permutations, show.time = "all", cor.type = "I", test = "LR", resamp = "pit.trap")
anova_time
########################################################



mod_prior <- manyglm(comm_all_drop_atrasado_mvabund ~ block2 + ( MDS1 + MDS2 ) + AM_days_sc + AM_days_sc_squared, family="negative.binomial",  data = predictors_nmds, composition = FALSE)

mod_no_prior <- manyglm(comm_all_drop_atrasado_mvabund ~ block2 + AM_days_sc + AM_days_sc_squared, family="negative.binomial",  data = predictors_nmds, composition = FALSE)

anova_prior <- anova(mod_no_prior, mod_prior, bootID = permutations, show.time = "all", cor.type = "I", test = "LR", resamp = "pit.trap")
anova_prior

########################################################
mod_no_int <- manyglm(comm_all_drop_atrasado_mvabund ~ block2 + ( MDS1 + MDS2 ) + AM_days_sc + AM_days_sc_squared, family="negative.binomial",  data = predictors_nmds, composition = FALSE)

mod_int <- manyglm(comm_all_drop_atrasado_mvabund ~ block2 + ( MDS1 + MDS2 ) + AM_days_sc + AM_days_sc_squared + AM_days_sc:( MDS1 + MDS2 ) + AM_days_sc_squared:( MDS1 + MDS2 ), family="negative.binomial",  data = predictors_nmds, composition = FALSE)

anova_interaction <- anova(mod_no_int, mod_int, bootID = permutations, show.time = "all", cor.type = "I", test = "LR", resamp = "pit.trap")
anova_interaction

```



Which are the species who have at least one of the coefficients for the effect of time in interaction with the effect of the first survey whose confidence interval do not include zero?

```{r}

coefs <- mod_int$coefficients
LCL <- coefs + mod_int$stderr.coefficients * qnorm(0.025) 
UCL <- coefs + mod_int$stderr.coefficients * qnorm(0.975) 

coefs[LCL < 0 &  UCL > 0] <- NA

coefs <- coefs[-c(1:7),]

coefs <- coefs[, colSums(coefs, na.rm = TRUE) != 0]

```


### Making predictions for plotting

```{r}

#High abundances of 
#Aedes
#Culex
#Dendropsophus_minutus
#Tanypodinae
#Callibaetis
#Culex

new_data_AB_high_MDS1_high_MDS2 <- 
  data.frame(AM_days_sc = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100),
                                AM_days_sc_squared = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100)^2,
                                block2 = factor(rep("AB", 100), levels = levels(as.factor(Exp_design_all_drop_atrasado$block2))),
             MDS1 = rep(quantile(predictors_nmds$MDS1, 0.9), 100),
             MDS2 = rep(quantile(predictors_nmds$MDS2, 0.9), 100))

new_data_CD_high_MDS1_high_MDS2 <- 
  data.frame(AM_days_sc = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100),
                                AM_days_sc_squared = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100)^2,
                                block2 = factor(rep("CD", 100), levels = levels(as.factor(Exp_design_all_drop_atrasado$block2))),
             MDS1 = rep(quantile(predictors_nmds$MDS1, 0.9), 100),
             MDS2 = rep(quantile(predictors_nmds$MDS2, 0.9), 100))


new_data_EF_high_MDS1_high_MDS2 <- 
  data.frame(AM_days_sc = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100),
                                AM_days_sc_squared = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100)^2,
                                block2 = factor(rep("EF", 100), levels = levels(as.factor(Exp_design_all_drop_atrasado$block2))),
             MDS1 = rep(quantile(predictors_nmds$MDS1, 0.9), 100),
             MDS2 = rep(quantile(predictors_nmds$MDS2, 0.9), 100))


###########################################################################################



new_data_AB_low_MDS1_high_MDS2 <- 
  data.frame(AM_days_sc = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100),
                                AM_days_sc_squared = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100)^2,
                                block2 = factor(rep("AB", 100), levels = levels(as.factor(Exp_design_all_drop_atrasado$block2))),
             MDS1 = rep(quantile(predictors_nmds$MDS1, 0.1), 100),
             MDS2 = rep(quantile(predictors_nmds$MDS2, 0.9), 100))

new_data_CD_low_MDS1_high_MDS2 <- 
  data.frame(AM_days_sc = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100),
                                AM_days_sc_squared = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100)^2,
                                block2 = factor(rep("CD", 100), levels = levels(as.factor(Exp_design_all_drop_atrasado$block2))),
             MDS1 = rep(quantile(predictors_nmds$MDS1, 0.1), 100),
             MDS2 = rep(quantile(predictors_nmds$MDS2, 0.9), 100))


new_data_EF_low_MDS1_high_MDS2 <- 
  data.frame(AM_days_sc = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100),
                                AM_days_sc_squared = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100)^2,
                                block2 = factor(rep("EF", 100), levels = levels(as.factor(Exp_design_all_drop_atrasado$block2))),
             MDS1 = rep(quantile(predictors_nmds$MDS1, 0.1), 100),
             MDS2 = rep(quantile(predictors_nmds$MDS2, 0.9), 100))


###########################################################################################




new_data_AB_low_MDS1_low_MDS2 <- 
  data.frame(AM_days_sc = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100),
                                AM_days_sc_squared = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100)^2,
                                block2 = factor(rep("AB", 100), levels = levels(as.factor(Exp_design_all_drop_atrasado$block2))),
             MDS1 = rep(quantile(predictors_nmds$MDS1, 0.1), 100),
             MDS2 = rep(quantile(predictors_nmds$MDS2, 0.1), 100))

new_data_CD_low_MDS1_low_MDS2 <- 
  data.frame(AM_days_sc = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100),
                                AM_days_sc_squared = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100)^2,
                                block2 = factor(rep("CD", 100), levels = levels(as.factor(Exp_design_all_drop_atrasado$block2))),
             MDS1 = rep(quantile(predictors_nmds$MDS1, 0.1), 100),
             MDS2 = rep(quantile(predictors_nmds$MDS2, 0.1), 100))


new_data_EF_low_MDS1_low_MDS2 <- 
  data.frame(AM_days_sc = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100),
                                AM_days_sc_squared = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100)^2,
                                block2 = factor(rep("EF", 100), levels = levels(as.factor(Exp_design_all_drop_atrasado$block2))),
             MDS1 = rep(quantile(predictors_nmds$MDS1, 0.1), 100),
             MDS2 = rep(quantile(predictors_nmds$MDS2, 0.1), 100))


###########################################################################################



new_data_AB_high_MDS1_low_MDS2 <- 
  data.frame(AM_days_sc = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100),
                                AM_days_sc_squared = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100)^2,
                                block2 = factor(rep("AB", 100), levels = levels(as.factor(Exp_design_all_drop_atrasado$block2))),
             MDS1 = rep(quantile(predictors_nmds$MDS1, 0.9), 100),
             MDS2 = rep(quantile(predictors_nmds$MDS2, 0.1), 100))

new_data_CD_high_MDS1_low_MDS2 <- 
  data.frame(AM_days_sc = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100),
                                AM_days_sc_squared = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100)^2,
                                block2 = factor(rep("CD", 100), levels = levels(as.factor(Exp_design_all_drop_atrasado$block2))),
             MDS1 = rep(quantile(predictors_nmds$MDS1, 0.9), 100),
             MDS2 = rep(quantile(predictors_nmds$MDS2, 0.1), 100))


new_data_EF_high_MDS1_low_MDS2 <- 
  data.frame(AM_days_sc = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100),
                                AM_days_sc_squared = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100)^2,
                                block2 = factor(rep("EF", 100), levels = levels(as.factor(Exp_design_all_drop_atrasado$block2))),
             MDS1 = rep(quantile(predictors_nmds$MDS1, 0.9), 100),
             MDS2 = rep(quantile(predictors_nmds$MDS2, 0.1), 100))


###########################################################################################





###########################################################################################


AB_high_MDS1_high_MDS2 <- predict.manyglm(mod_int, newdata = new_data_AB_high_MDS1_high_MDS2, type = "response")
CD_high_MDS1_high_MDS2 <- predict.manyglm(mod_int, newdata = new_data_CD_high_MDS1_high_MDS2, type = "response")
EF_high_MDS1_high_MDS2 <- predict.manyglm(mod_int, newdata = new_data_EF_high_MDS1_high_MDS2, type = "response")

high_MDS1_high_MDS2 <- array(NA, dim = c(nrow(AB_high_MDS1_high_MDS2), ncol(AB_high_MDS1_high_MDS2), 3))
high_MDS1_high_MDS2[,,1] <- AB_high_MDS1_high_MDS2
high_MDS1_high_MDS2[,,2] <- CD_high_MDS1_high_MDS2
high_MDS1_high_MDS2[,,3] <- EF_high_MDS1_high_MDS2

high_MDS1_high_MDS2_mean <- as.data.frame(apply(high_MDS1_high_MDS2, MARGIN = c(1,2), FUN = mean))
colnames(high_MDS1_high_MDS2_mean) <- colnames(AB_high_MDS1_high_MDS2)
high_MDS1_high_MDS2_mean






AB_low_MDS1_high_MDS2 <- predict.manyglm(mod_int, newdata = new_data_AB_low_MDS1_high_MDS2, type = "response")
CD_low_MDS1_high_MDS2 <- predict.manyglm(mod_int, newdata = new_data_CD_low_MDS1_high_MDS2, type = "response")
EF_low_MDS1_high_MDS2 <- predict.manyglm(mod_int, newdata = new_data_EF_low_MDS1_high_MDS2, type = "response")

low_MDS1_high_MDS2 <- array(NA, dim = c(nrow(AB_low_MDS1_high_MDS2), ncol(AB_low_MDS1_high_MDS2), 3))
low_MDS1_high_MDS2[,,1] <- AB_low_MDS1_high_MDS2
low_MDS1_high_MDS2[,,2] <- CD_low_MDS1_high_MDS2
low_MDS1_high_MDS2[,,3] <- EF_low_MDS1_high_MDS2

low_MDS1_high_MDS2_mean <- as.data.frame(apply(low_MDS1_high_MDS2, MARGIN = c(1,2), FUN = mean))
colnames(low_MDS1_high_MDS2_mean) <- colnames(AB_low_MDS1_high_MDS2)
low_MDS1_high_MDS2_mean





AB_high_MDS1_low_MDS2 <- predict.manyglm(mod_int, newdata = new_data_AB_high_MDS1_low_MDS2, type = "response")
CD_high_MDS1_low_MDS2 <- predict.manyglm(mod_int, newdata = new_data_CD_high_MDS1_low_MDS2, type = "response")
EF_high_MDS1_low_MDS2 <- predict.manyglm(mod_int, newdata = new_data_EF_high_MDS1_low_MDS2, type = "response")

high_MDS1_low_MDS2 <- array(NA, dim = c(nrow(AB_high_MDS1_low_MDS2), ncol(AB_high_MDS1_low_MDS2), 3))
high_MDS1_low_MDS2[,,1] <- AB_high_MDS1_low_MDS2
high_MDS1_low_MDS2[,,2] <- CD_high_MDS1_low_MDS2
high_MDS1_low_MDS2[,,3] <- EF_high_MDS1_low_MDS2

high_MDS1_low_MDS2_mean <- as.data.frame(apply(high_MDS1_low_MDS2, MARGIN = c(1,2), FUN = mean))
colnames(high_MDS1_low_MDS2_mean) <- colnames(AB_high_MDS1_low_MDS2)
high_MDS1_low_MDS2_mean




AB_low_MDS1_low_MDS2 <- predict.manyglm(mod_int, newdata = new_data_AB_low_MDS1_low_MDS2, type = "response")
CD_low_MDS1_low_MDS2 <- predict.manyglm(mod_int, newdata = new_data_CD_low_MDS1_low_MDS2, type = "response")
EF_low_MDS1_low_MDS2 <- predict.manyglm(mod_int, newdata = new_data_EF_low_MDS1_low_MDS2, type = "response")

low_MDS1_low_MDS2 <- array(NA, dim = c(nrow(AB_low_MDS1_low_MDS2), ncol(AB_low_MDS1_low_MDS2), 3))
low_MDS1_low_MDS2[,,1] <- AB_low_MDS1_low_MDS2
low_MDS1_low_MDS2[,,2] <- CD_low_MDS1_low_MDS2
low_MDS1_low_MDS2[,,3] <- EF_low_MDS1_low_MDS2

low_MDS1_low_MDS2_mean <- as.data.frame(apply(low_MDS1_low_MDS2, MARGIN = c(1,2), FUN = mean))
colnames(low_MDS1_low_MDS2_mean) <- colnames(AB_low_MDS1_low_MDS2)
low_MDS1_low_MDS2_mean




```



### Ploting predicted effects 


```{r,    fig.width = 10, fig.height = 12, dpi = 600}

sp_names <- colnames(high_MDS1_high_MDS2_mean)
sp_names <- gsub("\\.", " ", sp_names)

sp_fonts <- rep(3, ncol(high_MDS1_high_MDS2_mean))
sp_fonts[sp_names == "Chironominae" | sp_names == "Tanypodinae"] <- 1

sp_letters <- c("a)", "b)", "c)", "d)", "e)", "f)", "g)", "h)", "i)", "j)", "k)")


#svg(filename = "Plots/Community structure analysis/predicted_species_trajectories.svg", width = 10, height = 12, pointsize = 13)


close.screen(all.screens = TRUE)
split.screen(matrix(c(0,0.3333333,       0.75,1,
                      0.3333333,0.666666,0.75,1,
                      0.666666,1,        0.75,1,
                      0,0.3333333,       0.5,0.75,
                      0.3333333,0.666666,0.5,0.75,
                      0.666666,1,        0.5,0.75,
                      0,0.3333333,       0.25,0.5,
                      0.3333333,0.666666,0.25,0.5,
                      0.666666,1,        0.25,0.5,
                      0,0.3333333,       0,0.25,
                      0.3333333,0.666666,0,0.25,
                      0.666666,1,        0,0.25), ncol = 4, nrow = 12, byrow = TRUE))


for(i in 1:11){
  
screen(i)
  
par(mar = c(4,4,1,1), bty = "l")
  
ymax <- max(c(high_MDS1_high_MDS2_mean[,i], high_MDS1_low_MDS2_mean[,i], low_MDS1_high_MDS2_mean[,i], low_MDS1_low_MDS2_mean[,i]))*1.3

plot(NA, xlim = c(32 - 10, 158 + 10), ylim = c(0, ymax), xaxt = "n", yaxt = "n", xlab = "", ylab = "")

lines(y = high_MDS1_high_MDS2_mean[,i],                                                                                                                         x = seq(from = min(Exp_design_all_drop_atrasado$AM_days), to = max(Exp_design_all_drop_atrasado$AM_days), length.out = 100),
          col= "white", lwd = 3)
lines(y = high_MDS1_high_MDS2_mean[,i],
          x = seq(from = min(Exp_design_all_drop_atrasado$AM_days), to = max(Exp_design_all_drop_atrasado$AM_days), length.out = 100),
          col= "#56B4E9", lwd = 2)


lines(y = low_MDS1_high_MDS2_mean[,i],                                                                                                                    x = seq(from = min(Exp_design_all_drop_atrasado$AM_days), to = max(Exp_design_all_drop_atrasado$AM_days), length.out = 100),
          col= "white", lwd = 3)
lines(y = low_MDS1_high_MDS2_mean[,i],
          x = seq(from = min(Exp_design_all_drop_atrasado$AM_days), to = max(Exp_design_all_drop_atrasado$AM_days), length.out = 100),
          col= "#009E73", lwd = 2)


lines(y = high_MDS1_low_MDS2_mean[,i],                                                                                                                         x = seq(from = min(Exp_design_all_drop_atrasado$AM_days), to = max(Exp_design_all_drop_atrasado$AM_days), length.out = 100),
          col= "white", lwd = 3)
lines(y = high_MDS1_low_MDS2_mean[,i],
          x = seq(from = min(Exp_design_all_drop_atrasado$AM_days), to = max(Exp_design_all_drop_atrasado$AM_days), length.out = 100),
          col= "#CC79A7", lwd = 2)


lines(y = low_MDS1_low_MDS2_mean[,i],                                                                                                                         x = seq(from = min(Exp_design_all_drop_atrasado$AM_days), to = max(Exp_design_all_drop_atrasado$AM_days), length.out = 100),
          col= "white", lwd = 3)
lines(y = low_MDS1_low_MDS2_mean[,i],
          x = seq(from = min(Exp_design_all_drop_atrasado$AM_days), to = max(Exp_design_all_drop_atrasado$AM_days), length.out = 100),
          col= "#E69F00", lwd = 2)


axis(1, at = c(32, 80, 116, 158))
title(xlab = "Days", line = 2.5, cex.lab = 1.25)

axis(2, gap.axis = -10, las = 2)
#title(ylab = "Abundance of", line = 3.75, cex.lab = 1.25)
title(ylab = sp_names[i], line = 2.5, cex.lab = 1, font.lab = sp_fonts[i])

letters(x = 10, y = 97, sp_letters[i], cex = 1.5)

}

screen(12)

par(mar = c(0.1,0.1,0.1,0.1), bty = "n")
plot(NA, xlim = c(0, 100), ylim = c(0, 100), xaxt = "n", yaxt = "n", xlab = "", ylab = "")
legend(legend = c("High nMDS1, high nMDS2",
                 "High nMDS1, low nMDS2",
                  "Low nMDS1, high nMDS2",
                  "Low nMDS1, low nMDS2"), x = 50, y = 50, bty = "n", lty = 1, lwd = 3, col = c("#56B4E9", "#CC79A7", "#009E73","#E69F00"), xjust = 0.5, yjust = 0.5)

  
#dev.off()


```


### Plotting coefficients

```{r,    fig.width = 10, fig.height = 4.5, dpi = 600}

sp_names <- colnames(mod_int$coefficients)
sp_names <- gsub("\\.", " ", sp_names)

sp_names[sp_names == "Dendropsophus minutus"] <- "D. minutus"
sp_names[sp_names == "Scinax fuscovarius"] <- "S. fuscovarius"

sp_font <- rep(3, length(sp_names))
sp_font[sp_names == "Chironominae"] <- 1
sp_font[sp_names == "Tanypodinae"] <- 1

interaction_coefs <- data.frame(t(mod_int$coefficients[(nrow(mod_int$coefficients)-3):nrow(mod_int$coefficients),]))
interaction_coefs_se <- data.frame(t(mod_int$stderr.coefficients[(nrow(mod_int$stderr.coefficients)-3):nrow(mod_int$stderr.coefficients),]))

interaction_upper <- interaction_coefs + (interaction_coefs_se * qnorm(0.975))
interaction_lower <- interaction_coefs + (interaction_coefs_se * qnorm(0.025))


#svg(filename = "Plots/Community structure analysis/community_trajectories_coefs.svg", width = 10, height = 4.5, pointsize = 12)


close.screen(all.screens = TRUE)
split.screen(matrix(c(0 , 0.1, 0, 1  ,
                      0.1, 0.325, 0, 1,
                      0.325, 0.55, 0, 1,
                      0.55, 0.775, 0, 1,
                      0.775, 1, 0, 1), ncol = 4, nrow = 5, byrow = TRUE))


screen(2)
par(mar = c(4,2,2,0.5))

My_coefplot(mles = interaction_coefs$MDS1.AM_days_sc, upper = interaction_upper$MDS1.AM_days_sc,
            lower = interaction_lower$MDS1.AM_days_sc, col_sig = "red",
            cex_sig = 1.5, species_labels = sp_names, yaxis_font = sp_font, cex.axis = 0.9)
title(xlab = "nMDS1 : Time", cex.lab = 1, line = 2.5)
#screen(2, new = FALSE)
letters(x = 12, y = 94, "a)", cex = 1.5)

screen(3)
par(mar = c(4,2,2,0.5))

My_coefplot(mles = interaction_coefs$MDS2.AM_days_sc, upper = interaction_upper$MDS2.AM_days_sc,
            lower = interaction_lower$MDS2.AM_days_sc, col_sig = "red",
            cex_sig = 1.5, species_labels = FALSE, yaxis_font = sp_font, cex.axis = 0.9)
title(xlab = "nMDS2 : Time", cex.lab = 1, line = 2.5)
#screen(2, new = FALSE)
letters(x = 12, y = 94, "b)", cex = 1.5)

screen(4)
par(mar = c(4,2,2,0.5))

My_coefplot(mles = interaction_coefs$MDS1.AM_days_sc_squared, upper = interaction_upper$MDS1.AM_days_sc_squared,
            lower = interaction_lower$MDS1.AM_days_sc_squared, col_sig = "red",
            cex_sig = 1.5, species_labels = FALSE, yaxis_font = sp_font, cex.axis = 0.9, xlim = c(-2,5))
title(xlab = "nMDS1 : Time²", cex.lab = 1, line = 2.5)
#screen(2, new = FALSE)
letters(x = 12, y = 94, "c)", cex = 1.5)

screen(5)
par(mar = c(4,2,2,0.5))

My_coefplot(mles = interaction_coefs$MDS2.AM_days_sc_squared, upper = interaction_upper$MDS2.AM_days_sc_squared,
            lower = interaction_lower$MDS2.AM_days_sc_squared, col_sig = "red",
            cex_sig = 1.5, species_labels = FALSE, yaxis_font = sp_font, cex.axis = 0.9, xlim = c(-6,2))
title(xlab = "nMDS2 : Time²", cex.lab = 1, line = 2.5)
#screen(2, new = FALSE)
letters(x = 12, y = 94, "d)", cex = 1.5)

#dev.off()

```






```{r}

comm_trajectories <- rbind(high_MDS1_high_MDS2_mean, low_MDS1_high_MDS2_mean, high_MDS1_low_MDS2_mean, low_MDS1_low_MDS2_mean)

comm_trajectories_relative <- decostand(comm_trajectories, method = "total", MARGIN = 2)

set.seed(5); nmds_comm_trajectories <- metaMDS(comm_trajectories_relative, distance = "bray", k = 2, trymax  = 100, try = 100, engine = "monoMDS", autotransform  = FALSE)

nmds_comm_trajectories
```


```{r}
points_high_MDS1_high_MDS2 <- nmds_comm_trajectories$points[1:100,]
points_low_MDS1_high_MDS2 <- nmds_comm_trajectories$points[101:200,]
points_high_MDS1_low_MDS2 <- nmds_comm_trajectories$points[201:300,]
points_low_MDS1_low_MDS2 <- nmds_comm_trajectories$points[301:400,]

species_pred <- nmds_comm_trajectories$species
```




```{r}
find_day <- function(day, min, max, length = 100){
  
  new_day <- day - min
  range <- max - min
  
  result <- round((new_day*length)/range)
  
  if(result == 0){result <- 1}
  
  return(result)
  
}
```




```{r,    fig.width = 10, fig.height = 4.5, dpi = 600}
comm_AM1_nmds
species <- nmds_comm_AM1_rm_total$species

sp_names <- rownames(species)
sp_names <- gsub("\\.", " ", sp_names)



#svg(filename = "Plots/Community structure analysis/community_trajectories.svg", width = 10, height = 4.5, pointsize = 12)




close.screen(all.screens = TRUE)
split.screen(matrix(c(0  , 0.5, 0, 1  ,
                      0.5, 1  , 0, 1  ), ncol = 4, nrow = 2, byrow = TRUE))

screen(1)
par(mar = c(4,4,1,1), bty = "o")


xmin <- min(c(comm_AM1_nmds[,1], species[,1]))*1.2
xmax <- max(c(comm_AM1_nmds[,1], species[,1]))*1.2
ymin <- min(c(comm_AM1_nmds[,2], species[,2]))*1.2
ymax <- max(c(comm_AM1_nmds[,2], species[,2]))*1.2




plot(comm_AM1_nmds[,1], comm_AM1_nmds[,2], xlim = c(xmin,xmax), ylim = c(ymin, ymax),
     type = "n", xaxt = "n", yaxt = "n", ylab = "", xlab = "")


rect(xleft = 0, ybottom = 0, xright = xmax*1.2, ytop = ymax*1.2 ,col = transparent("#56B4E9", trans.val = 0.75), border = "white", lwd = 4)
rect(xleft = xmin*1.2, ybottom = ymin*1.2, xright = 0, ytop = 0,col = transparent("#E69F00", trans.val = 0.75), border = "white", lwd = 4)
rect(xleft = 0, ybottom = ymin*1.2, xright = xmax*1.2, ytop = 0,col = transparent("#CC79A7", trans.val = 0.75), border = "white", lwd = 4)
rect(xleft = xmin*1.2, ybottom = 0, xright = 0, ytop = ymax*1.2,col = transparent("#009E73", trans.val = 0.75), border = "white", lwd = 4)


abline(h = 0, v = 0, lty = 2)

library(scales)
library(shape)


#pal <- col_numeric(palette = c("white", "black"), domain = urb, na.color = "grey50", alpha = FALSE, reverse = FALSE)
#col <-pal(urb)

points(comm_AM1_nmds[,1],comm_AM1_nmds[,2], col = "grey70", bg = "white", pch = 16, cex = 1.5)

Arrows(x0 <- rep(0, nrow(species)),
       y0 <- rep(0, nrow(species)),
       x1 <- species[,1],
       y1 <- species[,2], arr.type = "triangle", arr.length = 0.4, col = "#C49C94", lwd = 1.5)

text(x = species[,1]*1.2, y = species[,2]*1.2, labels = sp_names, cex = 0.8, col = "black", font = 2)

axis(1, cex.axis = 1)
axis(2, cex.axis = 1, las = 2)
title(xlab = "nMDS 1", cex.lab = 1.2, line = 3)
title(ylab = "nMDS 2", cex.lab = 1.2, line = 3)
#title(main = "Morphological traits", line = 0.5, adj = 0, cex.main = 1.5)
letters(x = 10, y = 97, "a)", cex = 1.5)


screen(2)

#set.seed(1);species_pred <- jitter(species_pred, amount = 0.25)

xmin <- min(c(points_high_MDS1_high_MDS2[,1], points_low_MDS1_high_MDS2[,1], points_high_MDS1_low_MDS2[,1], points_low_MDS1_low_MDS2[,1],species_pred[,1]))*1.1
xmax <- max(c(points_high_MDS1_high_MDS2[,1], points_low_MDS1_high_MDS2[,1], points_high_MDS1_low_MDS2[,1], points_low_MDS1_low_MDS2[,1],species_pred[,1]))*1.1

ymin <- min(c(points_high_MDS1_high_MDS2[,2], points_low_MDS1_high_MDS2[,2], points_high_MDS1_low_MDS2[,2], points_low_MDS1_low_MDS2[,2],species_pred[,2]))*1.1
ymax <- max(c(points_high_MDS1_high_MDS2[,2], points_low_MDS1_high_MDS2[,2], points_high_MDS1_low_MDS2[,2], points_low_MDS1_low_MDS2[,2],species_pred[,2]))*1.1

par(mar = c(4, 4, 1, 1))
  
plot(NA, xlim = c(xmin, xmax), ylim = c(ymin, ymax), xlab = "", ylab = "", xaxt = "n", yaxt = "n")

lines(x = points_high_MDS1_high_MDS2[,1], y = points_high_MDS1_high_MDS2[,2], lwd = 3, lty = 1, col = "#56B4E9") #controle

lines(x = points_low_MDS1_high_MDS2[,1], y = points_low_MDS1_high_MDS2[,2], lwd = 3, lty = 1, col = "#009E73") #atrasado

lines(x = points_high_MDS1_low_MDS2[,1], y = points_high_MDS1_low_MDS2[,2], lwd = 3, lty = 1, col = "#CC79A7") #fechado

lines(x = points_low_MDS1_low_MDS2[,1], y = points_low_MDS1_low_MDS2[,2], lwd = 3, lty = 1, col = "#E69F00") #fechado



#####################################################################



##################################################

points(x = points_high_MDS1_high_MDS2[find_day(day = 32, min = 32, max = 158),1],
       y = points_high_MDS1_high_MDS2[find_day(day = 32, min = 32, max = 158),2],
       pch = 21, bg = "white", col = "#56B4E9", lwd = 3, cex = 3.5)

text(x = points_high_MDS1_high_MDS2[find_day(day = 32, min = 32, max = 158),1],
       y = points_high_MDS1_high_MDS2[find_day(day = 32, min = 32, max = 158),2], labels = "32", cex = 0.7, col = "#56B4E9", font = 2)

points(x = points_high_MDS1_high_MDS2[find_day(day = 80, min = 32, max = 158),1],
       y = points_high_MDS1_high_MDS2[find_day(day = 80, min = 32, max = 158),2],
       pch = 21, bg = "white", col = "#56B4E9", lwd = 3, cex = 3.5)

text(x = points_high_MDS1_high_MDS2[find_day(day = 80, min = 32, max = 158),1],
       y = points_high_MDS1_high_MDS2[find_day(day = 80, min = 32, max = 158),2], labels = "80", cex = 0.7, col = "#56B4E9", font = 2)

points(x = points_high_MDS1_high_MDS2[find_day(day = 116, min = 32, max = 158),1],
       y = points_high_MDS1_high_MDS2[find_day(day = 116, min = 32, max = 158),2],
       pch = 21, bg = "white", col = "#56B4E9", lwd = 3, cex = 3.5)

text(x = points_high_MDS1_high_MDS2[find_day(day = 116, min = 32, max = 158),1],
       y = points_high_MDS1_high_MDS2[find_day(day = 116, min = 32, max = 158),2], labels = "116", cex = 0.7, col = "#56B4E9", font = 2)

points(x = points_high_MDS1_high_MDS2[find_day(day = 158, min = 32, max = 158),1],
       y = points_high_MDS1_high_MDS2[find_day(day = 158, min = 32, max = 158),2],
       pch = 21, bg = "white", col = "#56B4E9", lwd = 3, cex = 3.5)

text(x = points_high_MDS1_high_MDS2[find_day(day = 158, min = 32, max = 158),1],
       y = points_high_MDS1_high_MDS2[find_day(day = 158, min = 32, max = 158),2], labels = "158", cex = 0.7, col = "#56B4E9", font = 2)
#################################################


##################################################

points(x = points_low_MDS1_high_MDS2[find_day(day = 32, min = 32, max = 158),1],
       y = points_low_MDS1_high_MDS2[find_day(day = 32, min = 32, max = 158),2],
       pch = 21, bg = "white", col = "#009E73", lwd = 3, cex = 3.5)

text(x = points_low_MDS1_high_MDS2[find_day(day = 32, min = 32, max = 158),1],
       y = points_low_MDS1_high_MDS2[find_day(day = 32, min = 32, max = 158),2], labels = "32", cex = 0.7, font = 2, col = "#009E73")

points(x = points_low_MDS1_high_MDS2[find_day(day = 80, min = 32, max = 158),1],
       y = points_low_MDS1_high_MDS2[find_day(day = 80, min = 32, max = 158),2],
       pch = 21, bg = "white", col = "#009E73", lwd = 3, cex = 3.5)

text(x = points_low_MDS1_high_MDS2[find_day(day = 80, min = 32, max = 158),1],
       y = points_low_MDS1_high_MDS2[find_day(day = 80, min = 32, max = 158),2], labels = "80", cex = 0.7, font = 2, col = "#009E73")

points(x = points_low_MDS1_high_MDS2[find_day(day = 116, min = 32, max = 158),1],
       y = points_low_MDS1_high_MDS2[find_day(day = 116, min = 32, max = 158),2],
       pch = 21, bg = "white", col = "#009E73", lwd = 3, cex = 3.5)

text(x = points_low_MDS1_high_MDS2[find_day(day = 116, min = 32, max = 158),1],
       y = points_low_MDS1_high_MDS2[find_day(day = 116, min = 32, max = 158),2], labels = "116", cex = 0.7, font = 2, col = "#009E73")

points(x = points_low_MDS1_high_MDS2[find_day(day = 158, min = 32, max = 158),1],
       y = points_low_MDS1_high_MDS2[find_day(day = 158, min = 32, max = 158),2],
       pch = 21, bg = "white", col = "#009E73", lwd = 3, cex = 3.5)

text(x = points_low_MDS1_high_MDS2[find_day(day = 158, min = 32, max = 158),1],
       y = points_low_MDS1_high_MDS2[find_day(day = 158, min = 32, max = 158),2], labels = "158", cex = 0.7, font = 2, col = "#009E73")
#################################################



##################################################

points(x = points_high_MDS1_low_MDS2[find_day(day = 32, min = 32, max = 158),1],
       y = points_high_MDS1_low_MDS2[find_day(day = 32, min = 32, max = 158),2],
       pch = 21, bg = "white", col = "#CC79A7", lwd = 3, cex = 3.5)

text(x = points_high_MDS1_low_MDS2[find_day(day = 32, min = 32, max = 158),1],
       y = points_high_MDS1_low_MDS2[find_day(day = 32, min = 32, max = 158),2], labels = "32", cex = 0.7, font = 2, col = "#CC79A7")

points(x = points_high_MDS1_low_MDS2[find_day(day = 80, min = 32, max = 158),1],
       y = points_high_MDS1_low_MDS2[find_day(day = 80, min = 32, max = 158),2],
       pch = 21, bg = "white", col = "#CC79A7", lwd = 3, cex = 3.5)

text(x = points_high_MDS1_low_MDS2[find_day(day = 80, min = 32, max = 158),1],
       y = points_high_MDS1_low_MDS2[find_day(day = 80, min = 32, max = 158),2], labels = "80", cex = 0.7, font = 2, col = "#CC79A7")

points(x = points_high_MDS1_low_MDS2[find_day(day = 116, min = 32, max = 158),1],
       y = points_high_MDS1_low_MDS2[find_day(day = 116, min = 32, max = 158),2],
       pch = 21, bg = "white", col = "#CC79A7", lwd = 3, cex = 3.5)

text(x = points_high_MDS1_low_MDS2[find_day(day = 116, min = 32, max = 158),1],
       y = points_high_MDS1_low_MDS2[find_day(day = 116, min = 32, max = 158),2], labels = "116", cex = 0.7, font = 2, col = "#CC79A7")

points(x = points_high_MDS1_low_MDS2[find_day(day = 158, min = 32, max = 158),1],
       y = points_high_MDS1_low_MDS2[find_day(day = 158, min = 32, max = 158),2],
       pch = 21, bg = "white", col = "#CC79A7", lwd = 3, cex = 3.5)

text(x = points_high_MDS1_low_MDS2[find_day(day = 158, min = 32, max = 158),1],
       y = points_high_MDS1_low_MDS2[find_day(day = 158, min = 32, max = 158),2], labels = "158", cex = 0.7, font = 2, col = "#CC79A7")
#################################################





##################################################

points(x = points_low_MDS1_low_MDS2[find_day(day = 32, min = 32, max = 158),1],
       y = points_low_MDS1_low_MDS2[find_day(day = 32, min = 32, max = 158),2],
       pch = 21, bg = "white", col = "#E69F00", lwd = 3, cex = 3.5)

text(x = points_low_MDS1_low_MDS2[find_day(day = 32, min = 32, max = 158),1],
       y = points_low_MDS1_low_MDS2[find_day(day = 32, min = 32, max = 158),2], labels = "32", cex = 0.7, font = 2, col = "#E69F00")

points(x = points_low_MDS1_low_MDS2[find_day(day = 80, min = 32, max = 158),1],
       y = points_low_MDS1_low_MDS2[find_day(day = 80, min = 32, max = 158),2],
       pch = 21, bg = "white", col = "#E69F00", lwd = 3, cex = 3.5)

text(x = points_low_MDS1_low_MDS2[find_day(day = 80, min = 32, max = 158),1],
       y = points_low_MDS1_low_MDS2[find_day(day = 80, min = 32, max = 158),2], labels = "80", cex = 0.7, font = 2, col = "#E69F00")

points(x = points_low_MDS1_low_MDS2[find_day(day = 116, min = 32, max = 158),1],
       y = points_low_MDS1_low_MDS2[find_day(day = 116, min = 32, max = 158),2],
       pch = 21, bg = "white", col = "#E69F00", lwd = 3, cex = 3.5)

text(x = points_low_MDS1_low_MDS2[find_day(day = 116, min = 32, max = 158),1],
       y = points_low_MDS1_low_MDS2[find_day(day = 116, min = 32, max = 158),2], labels = "116", cex = 0.7, font = 2, col = "#E69F00")

points(x = points_low_MDS1_low_MDS2[find_day(day = 158, min = 32, max = 158),1],
       y = points_low_MDS1_low_MDS2[find_day(day = 158, min = 32, max = 158),2],
       pch = 21, bg = "white", col = "#E69F00", lwd = 3, cex = 3.5)

text(x = points_low_MDS1_low_MDS2[find_day(day = 158, min = 32, max = 158),1],
       y = points_low_MDS1_low_MDS2[find_day(day = 158, min = 32, max = 158),2], labels = "158", cex = 0.7, font = 2, col = "#E69F00")
#################################################



########################## species_pred #################################


sp_names <- rownames(species_pred)
sp_names <- substr(sp_names, start = 1, stop = 3)


for(i in 1:nrow(species_pred)){
  #points(x = species_pred[i,1],
   #    y = species_pred[i,2],
    #   pch = 21, bg = "white", col = "grey50", lwd = 2, cex = 4)

text_contour(x = species_pred[i,1],
       y = species_pred[i,2], labels = sp_names[i], cex = 0.8, col = "white", thick = 0.004)
  
text(x = species_pred[i,1],
       y = species_pred[i,2], labels = sp_names[i], cex = 0.8, col = "grey30")
}




axis(1)
axis(2, cex.axis = 1, las = 2)

title(xlab = "nMDS 1", line = 3, cex.lab = 1.2)
title(ylab = "nMDS 2", line = 3, cex.lab = 1.2)

letters(x = 10, y = 97, "b)", cex = 1.5)


#par(new = TRUE)
#plot(NA, xlim = c(0, 100), ylim = c(0, 100), xlab = "", ylab = "", xaxt = "n", yaxt = "n", bty = "n")

#legend(x = 100, y = 100, xjust = 1, yjust = 1, lty = c(1,1,1), lwd = 3, legend = c("Control", "Closed", "Late"), col = c("#009E73", "#56B4E9","#D55E00"), bty = "n")

#dev.off()


```





## Using treatments to describe initial communities.



### Testing for effects

```{r}

nrow(predictors_nmds)
nrow(comm_all_drop_atrasado_rm)

set.seed(3)
control <- permute::how(within = permute::Within(type = 'free'),
                        plots = Plots(strata = predictors_nmds$sites, type = 'free'),
                        nperm = 999)
permutations <- shuffleSet(nrow(comm_all_drop_atrasado_rm), control = control)


comm_all_drop_atrasado_mvabund <- mvabund(comm_all_drop_atrasado_rm)

mod_full_lin <- manyglm(comm_all_drop_atrasado_mvabund ~ block2 + treatments  + AM_days_sc + AM_days_sc:treatments, family="negative.binomial",  data = predictors_nmds, composition = FALSE)

mod_full_quad <- manyglm(comm_all_drop_atrasado_mvabund ~ block2 + treatments + AM_days_sc + AM_days_sc_squared + AM_days_sc:treatments + AM_days_sc_squared:treatments, family="negative.binomial",  data = predictors_nmds, composition = FALSE)

anova_quadratic_test <- anova(mod_full_lin, mod_full_quad, bootID = permutations, show.time = "all", cor.type = "I", test = "LR", resamp = "pit.trap")
anova_quadratic_test


########################################################
mod_block <- manyglm(comm_all_drop_atrasado_mvabund ~ block2 + treatments + AM_days_sc + AM_days_sc_squared, family="negative.binomial",  data = predictors_nmds, composition = FALSE)

mod_no_block <- manyglm(comm_all_drop_atrasado_mvabund ~ treatments + AM_days_sc + AM_days_sc_squared, family="negative.binomial",  data = predictors_nmds, composition = FALSE)

anova_block <- anova(mod_no_block, mod_block, bootID = permutations, show.time = "all", cor.type = "I", test = "LR", resamp = "pit.trap")
anova_block
########################################################






mod_time <- manyglm(comm_all_drop_atrasado_mvabund ~ block2 + treatments + AM_days_sc + AM_days_sc_squared, family="negative.binomial",  data = predictors_nmds, composition = FALSE)

mod_no_time <- manyglm(comm_all_drop_atrasado_mvabund ~ block2 + treatments, family="negative.binomial",  data = predictors_nmds, composition = FALSE)

anova_time <- anova(mod_no_time, mod_time, bootID = permutations, show.time = "all", cor.type = "I", test = "LR", resamp = "pit.trap")
anova_time
########################################################



mod_prior <- manyglm(comm_all_drop_atrasado_mvabund ~ block2 + treatments + AM_days_sc + AM_days_sc_squared, family="negative.binomial",  data = predictors_nmds, composition = FALSE)

mod_no_prior <- manyglm(comm_all_drop_atrasado_mvabund ~ block2 + AM_days_sc + AM_days_sc_squared, family="negative.binomial",  data = predictors_nmds, composition = FALSE)

anova_prior <- anova(mod_no_prior, mod_prior, bootID = permutations, show.time = "all", cor.type = "I", test = "LR", resamp = "pit.trap")
anova_prior

########################################################
mod_no_int <- manyglm(comm_all_drop_atrasado_mvabund ~ block2 + treatments + AM_days_sc + AM_days_sc_squared, family="negative.binomial",  data = predictors_nmds, composition = FALSE)

mod_int <- manyglm(comm_all_drop_atrasado_mvabund ~ block2 + treatments + AM_days_sc + AM_days_sc_squared + AM_days_sc:treatments + AM_days_sc_squared:treatments, family="negative.binomial",  data = predictors_nmds, composition = FALSE)

anova_interaction <- anova(mod_no_int, mod_int, bootID = permutations, show.time = "all", cor.type = "I", test = "LR", resamp = "pit.trap")
anova_interaction


########################################################


## Just out of curiosity, lets see if there is any interaction effec of time effects with blocks
########################################################
mod_block <- manyglm(comm_all_drop_atrasado_mvabund ~ block2 + treatments + AM_days_sc + AM_days_sc_squared, family="negative.binomial",  data = predictors_nmds, composition = FALSE)

mod_block_int <- manyglm(comm_all_drop_atrasado_mvabund ~ block2 + treatments + AM_days_sc + AM_days_sc_squared + AM_days_sc:block2 + AM_days_sc_squared:block2, family="negative.binomial",  data = predictors_nmds, composition = FALSE)

anova_block <- anova(mod_block, mod_block_int, bootID = permutations, show.time = "all", cor.type = "I", test = "LR", resamp = "pit.trap")
anova_block
########################################################


```



### Making predictions for plotting

```{r}

#High abundances of 
#Aedes
#Culex
#Dendropsophus_minutus
#Tanypodinae
#Callibaetis
#Culex

new_data_AB_control <- 
  data.frame(AM_days_sc = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100),
                                AM_days_sc_squared = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100)^2,
                                block2 = factor(rep("AB", 100), levels = levels(as.factor(Exp_design_all_drop_atrasado$block2))),
                                treatments = factor(rep("controle", 100), levels = levels(as.factor(Exp_design_all_drop_atrasado$treatments))))

new_data_CD_control <- 
  data.frame(AM_days_sc = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100),
                                AM_days_sc_squared = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100)^2,
                                block2 = factor(rep("CD", 100), levels = levels(as.factor(Exp_design_all_drop_atrasado$block2))),
             treatments = factor(rep("controle", 100), levels = levels(as.factor(Exp_design_all_drop_atrasado$treatments))))


new_data_EF_control <- 
  data.frame(AM_days_sc = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100),
                                AM_days_sc_squared = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100)^2,
                                block2 = factor(rep("EF", 100), levels = levels(as.factor(Exp_design_all_drop_atrasado$block2))),
             treatments = factor(rep("controle", 100), levels = levels(as.factor(Exp_design_all_drop_atrasado$treatments))))


###########################################################################################



new_data_AB_fechado <- 
  data.frame(AM_days_sc = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100),
                                AM_days_sc_squared = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100)^2,
                                block2 = factor(rep("AB", 100), levels = levels(as.factor(Exp_design_all_drop_atrasado$block2))),
                                treatments = factor(rep("fechado", 100), levels = levels(as.factor(Exp_design_all_drop_atrasado$treatments))))

new_data_CD_fechado <- 
  data.frame(AM_days_sc = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100),
                                AM_days_sc_squared = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100)^2,
                                block2 = factor(rep("CD", 100), levels = levels(as.factor(Exp_design_all_drop_atrasado$block2))),
             treatments = factor(rep("fechado", 100), levels = levels(as.factor(Exp_design_all_drop_atrasado$treatments))))


new_data_EF_fechado <- 
  data.frame(AM_days_sc = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100),
                                AM_days_sc_squared = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100)^2,
                                block2 = factor(rep("EF", 100), levels = levels(as.factor(Exp_design_all_drop_atrasado$block2))),
             treatments = factor(rep("fechado", 100), levels = levels(as.factor(Exp_design_all_drop_atrasado$treatments))))



###########################################################################################


new_data_AB_fechado_dia <- 
  data.frame(AM_days_sc = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100),
                                AM_days_sc_squared = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100)^2,
                                block2 = factor(rep("AB", 100), levels = levels(as.factor(Exp_design_all_drop_atrasado$block2))),
                                treatments = factor(rep("fechado_dia", 100), levels = levels(as.factor(Exp_design_all_drop_atrasado$treatments))))

new_data_CD_fechado_dia <- 
  data.frame(AM_days_sc = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100),
                                AM_days_sc_squared = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100)^2,
                                block2 = factor(rep("CD", 100), levels = levels(as.factor(Exp_design_all_drop_atrasado$block2))),
             treatments = factor(rep("fechado_dia", 100), levels = levels(as.factor(Exp_design_all_drop_atrasado$treatments))))


new_data_EF_fechado_dia <- 
  data.frame(AM_days_sc = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100),
                                AM_days_sc_squared = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100)^2,
                                block2 = factor(rep("EF", 100), levels = levels(as.factor(Exp_design_all_drop_atrasado$block2))),
             treatments = factor(rep("fechado_dia", 100), levels = levels(as.factor(Exp_design_all_drop_atrasado$treatments))))


###########################################################################################




new_data_AB_fechado_noite <- 
  data.frame(AM_days_sc = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100),
                                AM_days_sc_squared = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100)^2,
                                block2 = factor(rep("AB", 100), levels = levels(as.factor(Exp_design_all_drop_atrasado$block2))),
                                treatments = factor(rep("fechado_noite", 100), levels = levels(as.factor(Exp_design_all_drop_atrasado$treatments))))

new_data_CD_fechado_noite <- 
  data.frame(AM_days_sc = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100),
                                AM_days_sc_squared = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100)^2,
                                block2 = factor(rep("CD", 100), levels = levels(as.factor(Exp_design_all_drop_atrasado$block2))),
             treatments = factor(rep("fechado_noite", 100), levels = levels(as.factor(Exp_design_all_drop_atrasado$treatments))))


new_data_EF_fechado_noite <- 
  data.frame(AM_days_sc = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100),
                                AM_days_sc_squared = seq(from = min(Exp_design_all_drop_atrasado$AM_days_sc), to = max(Exp_design_all_drop_atrasado$AM_days_sc), length.out = 100)^2,
                                block2 = factor(rep("EF", 100), levels = levels(as.factor(Exp_design_all_drop_atrasado$block2))),
             treatments = factor(rep("fechado_noite", 100), levels = levels(as.factor(Exp_design_all_drop_atrasado$treatments))))


###########################################################################################





###########################################################################################


AB_control <- predict.manyglm(mod_int, newdata = new_data_AB_control, type = "response")
CD_control <- predict.manyglm(mod_int, newdata = new_data_CD_control, type = "response")
EF_control <- predict.manyglm(mod_int, newdata = new_data_EF_control, type = "response")

control <- array(NA, dim = c(nrow(AB_control), ncol(AB_control), 3))
control[,,1] <- AB_control
control[,,2] <- CD_control
control[,,3] <- EF_control

control_mean <- as.data.frame(apply(control, MARGIN = c(1,2), FUN = mean))
colnames(control_mean) <- colnames(AB_control)
control_mean




AB_fechado <- predict.manyglm(mod_int, newdata = new_data_AB_fechado, type = "response")
CD_fechado <- predict.manyglm(mod_int, newdata = new_data_CD_fechado, type = "response")
EF_fechado <- predict.manyglm(mod_int, newdata = new_data_EF_fechado, type = "response")

fechado <- array(NA, dim = c(nrow(AB_fechado), ncol(AB_fechado), 3))
fechado[,,1] <- AB_fechado
fechado[,,2] <- CD_fechado
fechado[,,3] <- EF_fechado

fechado_mean <- as.data.frame(apply(fechado, MARGIN = c(1,2), FUN = mean))
colnames(fechado_mean) <- colnames(AB_fechado)
fechado_mean



AB_fechado_dia <- predict.manyglm(mod_int, newdata = new_data_AB_fechado_dia, type = "response")
CD_fechado_dia <- predict.manyglm(mod_int, newdata = new_data_CD_fechado_dia, type = "response")
EF_fechado_dia <- predict.manyglm(mod_int, newdata = new_data_EF_fechado_dia, type = "response")

fechado_dia <- array(NA, dim = c(nrow(AB_fechado_dia), ncol(AB_fechado_dia), 3))
fechado_dia[,,1] <- AB_fechado_dia
fechado_dia[,,2] <- CD_fechado_dia
fechado_dia[,,3] <- EF_fechado_dia

fechado_dia_mean <- as.data.frame(apply(fechado_dia, MARGIN = c(1,2), FUN = mean))
colnames(fechado_dia_mean) <- colnames(AB_fechado_dia)
fechado_dia_mean



AB_fechado_noite <- predict.manyglm(mod_int, newdata = new_data_AB_fechado_noite, type = "response")
CD_fechado_noite <- predict.manyglm(mod_int, newdata = new_data_CD_fechado_noite, type = "response")
EF_fechado_noite <- predict.manyglm(mod_int, newdata = new_data_EF_fechado_noite, type = "response")

fechado_noite <- array(NA, dim = c(nrow(AB_fechado_noite), ncol(AB_fechado_noite), 3))
fechado_noite[,,1] <- AB_fechado_noite
fechado_noite[,,2] <- CD_fechado_noite
fechado_noite[,,3] <- EF_fechado_noite

fechado_noite_mean <- as.data.frame(apply(fechado_noite, MARGIN = c(1,2), FUN = mean))
colnames(fechado_noite_mean) <- colnames(AB_fechado_noite)
fechado_noite_mean





```






### Ploting predicted effects 


```{r,    fig.width = 10, fig.height = 12, dpi = 600}

sp_names <- colnames(control_mean)
sp_names <- gsub("\\.", " ", sp_names)

sp_fonts <- rep(3, ncol(control_mean))
sp_fonts[sp_names == "Chironominae" | sp_names == "Tanypodinae"] <- 1

sp_letters <- c("a)", "b)", "c)", "d)", "e)", "f)", "g)", "h)", "i)", "j)", "k)")


#svg(filename = "Plots/Community structure analysis/predicted_species_trajectories.svg", width = 10, height = 12, pointsize = 13)


close.screen(all.screens = TRUE)
split.screen(matrix(c(0,0.3333333,       0.75,1,
                      0.3333333,0.666666,0.75,1,
                      0.666666,1,        0.75,1,
                      0,0.3333333,       0.5,0.75,
                      0.3333333,0.666666,0.5,0.75,
                      0.666666,1,        0.5,0.75,
                      0,0.3333333,       0.25,0.5,
                      0.3333333,0.666666,0.25,0.5,
                      0.666666,1,        0.25,0.5,
                      0,0.3333333,       0,0.25,
                      0.3333333,0.666666,0,0.25,
                      0.666666,1,        0,0.25), ncol = 4, nrow = 12, byrow = TRUE))


for(i in 1:11){
  
screen(i)
  
par(mar = c(4,4,1,1), bty = "l")
  
ymax <- max(c(control_mean[,i], fechado_mean[,i], fechado_dia_mean[,i], fechado_noite_mean[,i]))*1.3

plot(NA, xlim = c(32 - 10, 158 + 10), ylim = c(0, ymax), xaxt = "n", yaxt = "n", xlab = "", ylab = "")

lines(y = control_mean[,i],                                                                                                                         x = seq(from = min(Exp_design_all_drop_atrasado$AM_days), to = max(Exp_design_all_drop_atrasado$AM_days), length.out = 100),
          col= "white", lwd = 3)
lines(y = control_mean[,i],
          x = seq(from = min(Exp_design_all_drop_atrasado$AM_days), to = max(Exp_design_all_drop_atrasado$AM_days), length.out = 100),
          col= "#56B4E9", lwd = 2)


lines(y = fechado_mean[,i],                                                                                                                    x = seq(from = min(Exp_design_all_drop_atrasado$AM_days), to = max(Exp_design_all_drop_atrasado$AM_days), length.out = 100),
          col= "white", lwd = 3)
lines(y = fechado_mean[,i],
          x = seq(from = min(Exp_design_all_drop_atrasado$AM_days), to = max(Exp_design_all_drop_atrasado$AM_days), length.out = 100),
          col= "#009E73", lwd = 2)


lines(y = fechado_dia_mean[,i],                                                                                                                         x = seq(from = min(Exp_design_all_drop_atrasado$AM_days), to = max(Exp_design_all_drop_atrasado$AM_days), length.out = 100),
          col= "white", lwd = 3)
lines(y = fechado_dia_mean[,i],
          x = seq(from = min(Exp_design_all_drop_atrasado$AM_days), to = max(Exp_design_all_drop_atrasado$AM_days), length.out = 100),
          col= "#CC79A7", lwd = 2)


lines(y = fechado_noite_mean[,i],                                                                                                                         x = seq(from = min(Exp_design_all_drop_atrasado$AM_days), to = max(Exp_design_all_drop_atrasado$AM_days), length.out = 100),
          col= "white", lwd = 3)
lines(y = fechado_noite_mean[,i],
          x = seq(from = min(Exp_design_all_drop_atrasado$AM_days), to = max(Exp_design_all_drop_atrasado$AM_days), length.out = 100),
          col= "#E69F00", lwd = 2)


axis(1, at = c(32, 80, 116, 158))
title(xlab = "Days", line = 2.5, cex.lab = 1.25)

axis(2, gap.axis = -10, las = 2)
#title(ylab = "Abundance of", line = 3.75, cex.lab = 1.25)
title(ylab = sp_names[i], line = 2.5, cex.lab = 1, font.lab = sp_fonts[i])

letters(x = 10, y = 97, sp_letters[i], cex = 1.5)

}

screen(12)

par(mar = c(0.1,0.1,0.1,0.1), bty = "n")
plot(NA, xlim = c(0, 100), ylim = c(0, 100), xaxt = "n", yaxt = "n", xlab = "", ylab = "")
legend(legend = c("Control",
                 "Closed",
                  "Dragonfly excl.",
                  "Amphibian excl."), x = 50, y = 50, bty = "n", lty = 1, lwd = 3, col = c("#56B4E9", "#009E73","#CC79A7","#E69F00"), xjust = 0.5, yjust = 0.5)

  
#dev.off()


```












```{r}

comm_trajectories <- rbind(control_mean, fechado_mean, fechado_dia_mean, fechado_noite_mean)

comm_trajectories_relative <- decostand(comm_trajectories, method = "total", MARGIN = 2)

set.seed(5); nmds_comm_trajectories <- metaMDS(comm_trajectories_relative, distance = "bray", k = 2, trymax  = 100, try = 100, engine = "monoMDS", autotransform  = FALSE)

nmds_comm_trajectories
```


```{r}
points_control <- nmds_comm_trajectories$points[1:100,]
points_fechado <- nmds_comm_trajectories$points[101:200,]
points_fechado_dia <- nmds_comm_trajectories$points[201:300,]
points_fechado_noite <- nmds_comm_trajectories$points[301:400,]

species_pred <- nmds_comm_trajectories$species
```




```{r}
find_day <- function(day, min, max, length = 100){
  
  new_day <- day - min
  range <- max - min
  
  result <- round((new_day*length)/range)
  
  if(result == 0){result <- 1}
  
  return(result)
  
}
```




```{r,    fig.width = 5, fig.height = 4.5, dpi = 600}


#screen(2)

#set.seed(1);species_pred <- jitter(species_pred, amount = 0.25)

xmin <- min(c(points_control[,1], points_fechado[,1], points_fechado_dia[,1], points_fechado_noite[,1],species_pred[,1]))*1.1
xmax <- max(c(points_control[,1], points_fechado[,1], points_fechado_dia[,1], points_fechado_noite[,1],species_pred[,1]))*1.1

ymin <- min(c(points_control[,2], points_fechado[,2], points_fechado_dia[,2], points_fechado_noite[,2],species_pred[,2]))*1.1
ymax <- max(c(points_control[,2], points_fechado[,2], points_fechado_dia[,2], points_fechado_noite[,2],species_pred[,2]))*1.1

par(mar = c(4, 4, 1, 1))
  
plot(NA, xlim = c(xmin, xmax), ylim = c(ymin, ymax), xlab = "", ylab = "", xaxt = "n", yaxt = "n")

lines(x = points_control[,1], y = points_control[,2], lwd = 3, lty = 1, col = "#56B4E9") #controle

lines(x = points_fechado[,1], y = points_fechado[,2], lwd = 3, lty = 1, col = "#009E73") #atrasado

lines(x = points_fechado_dia[,1], y = points_fechado_dia[,2], lwd = 3, lty = 1, col = "#CC79A7") #fechado

lines(x = points_fechado_noite[,1], y = points_fechado_noite[,2], lwd = 3, lty = 1, col = "#E69F00") #fechado



#####################################################################



##################################################

points(x = points_control[find_day(day = 32, min = 32, max = 158),1],
       y = points_control[find_day(day = 32, min = 32, max = 158),2],
       pch = 21, bg = "white", col = "#56B4E9", lwd = 3, cex = 3.5)

text(x = points_control[find_day(day = 32, min = 32, max = 158),1],
       y = points_control[find_day(day = 32, min = 32, max = 158),2], labels = "32", cex = 0.7, col = "#56B4E9", font = 2)

points(x = points_control[find_day(day = 80, min = 32, max = 158),1],
       y = points_control[find_day(day = 80, min = 32, max = 158),2],
       pch = 21, bg = "white", col = "#56B4E9", lwd = 3, cex = 3.5)

text(x = points_control[find_day(day = 80, min = 32, max = 158),1],
       y = points_control[find_day(day = 80, min = 32, max = 158),2], labels = "80", cex = 0.7, col = "#56B4E9", font = 2)

points(x = points_control[find_day(day = 116, min = 32, max = 158),1],
       y = points_control[find_day(day = 116, min = 32, max = 158),2],
       pch = 21, bg = "white", col = "#56B4E9", lwd = 3, cex = 3.5)

text(x = points_control[find_day(day = 116, min = 32, max = 158),1],
       y = points_control[find_day(day = 116, min = 32, max = 158),2], labels = "116", cex = 0.7, col = "#56B4E9", font = 2)

points(x = points_control[find_day(day = 158, min = 32, max = 158),1],
       y = points_control[find_day(day = 158, min = 32, max = 158),2],
       pch = 21, bg = "white", col = "#56B4E9", lwd = 3, cex = 3.5)

text(x = points_control[find_day(day = 158, min = 32, max = 158),1],
       y = points_control[find_day(day = 158, min = 32, max = 158),2], labels = "158", cex = 0.7, col = "#56B4E9", font = 2)
#################################################


##################################################

points(x = points_fechado[find_day(day = 32, min = 32, max = 158),1],
       y = points_fechado[find_day(day = 32, min = 32, max = 158),2],
       pch = 21, bg = "white", col = "#009E73", lwd = 3, cex = 3.5)

text(x = points_fechado[find_day(day = 32, min = 32, max = 158),1],
       y = points_fechado[find_day(day = 32, min = 32, max = 158),2], labels = "32", cex = 0.7, font = 2, col = "#009E73")

points(x = points_fechado[find_day(day = 80, min = 32, max = 158),1],
       y = points_fechado[find_day(day = 80, min = 32, max = 158),2],
       pch = 21, bg = "white", col = "#009E73", lwd = 3, cex = 3.5)

text(x = points_fechado[find_day(day = 80, min = 32, max = 158),1],
       y = points_fechado[find_day(day = 80, min = 32, max = 158),2], labels = "80", cex = 0.7, font = 2, col = "#009E73")

points(x = points_fechado[find_day(day = 116, min = 32, max = 158),1],
       y = points_fechado[find_day(day = 116, min = 32, max = 158),2],
       pch = 21, bg = "white", col = "#009E73", lwd = 3, cex = 3.5)

text(x = points_fechado[find_day(day = 116, min = 32, max = 158),1],
       y = points_fechado[find_day(day = 116, min = 32, max = 158),2], labels = "116", cex = 0.7, font = 2, col = "#009E73")

points(x = points_fechado[find_day(day = 158, min = 32, max = 158),1],
       y = points_fechado[find_day(day = 158, min = 32, max = 158),2],
       pch = 21, bg = "white", col = "#009E73", lwd = 3, cex = 3.5)

text(x = points_fechado[find_day(day = 158, min = 32, max = 158),1],
       y = points_fechado[find_day(day = 158, min = 32, max = 158),2], labels = "158", cex = 0.7, font = 2, col = "#009E73")
#################################################



##################################################

points(x = points_fechado_dia[find_day(day = 32, min = 32, max = 158),1],
       y = points_fechado_dia[find_day(day = 32, min = 32, max = 158),2],
       pch = 21, bg = "white", col = "#CC79A7", lwd = 3, cex = 3.5)

text(x = points_fechado_dia[find_day(day = 32, min = 32, max = 158),1],
       y = points_fechado_dia[find_day(day = 32, min = 32, max = 158),2], labels = "32", cex = 0.7, font = 2, col = "#CC79A7")

points(x = points_fechado_dia[find_day(day = 80, min = 32, max = 158),1],
       y = points_fechado_dia[find_day(day = 80, min = 32, max = 158),2],
       pch = 21, bg = "white", col = "#CC79A7", lwd = 3, cex = 3.5)

text(x = points_fechado_dia[find_day(day = 80, min = 32, max = 158),1],
       y = points_fechado_dia[find_day(day = 80, min = 32, max = 158),2], labels = "80", cex = 0.7, font = 2, col = "#CC79A7")

points(x = points_fechado_dia[find_day(day = 116, min = 32, max = 158),1],
       y = points_fechado_dia[find_day(day = 116, min = 32, max = 158),2],
       pch = 21, bg = "white", col = "#CC79A7", lwd = 3, cex = 3.5)

text(x = points_fechado_dia[find_day(day = 116, min = 32, max = 158),1],
       y = points_fechado_dia[find_day(day = 116, min = 32, max = 158),2], labels = "116", cex = 0.7, font = 2, col = "#CC79A7")

points(x = points_fechado_dia[find_day(day = 158, min = 32, max = 158),1],
       y = points_fechado_dia[find_day(day = 158, min = 32, max = 158),2],
       pch = 21, bg = "white", col = "#CC79A7", lwd = 3, cex = 3.5)

text(x = points_fechado_dia[find_day(day = 158, min = 32, max = 158),1],
       y = points_fechado_dia[find_day(day = 158, min = 32, max = 158),2], labels = "158", cex = 0.7, font = 2, col = "#CC79A7")
#################################################





##################################################

points(x = points_fechado_noite[find_day(day = 32, min = 32, max = 158),1],
       y = points_fechado_noite[find_day(day = 32, min = 32, max = 158),2],
       pch = 21, bg = "white", col = "#E69F00", lwd = 3, cex = 3.5)

text(x = points_fechado_noite[find_day(day = 32, min = 32, max = 158),1],
       y = points_fechado_noite[find_day(day = 32, min = 32, max = 158),2], labels = "32", cex = 0.7, font = 2, col = "#E69F00")

points(x = points_fechado_noite[find_day(day = 80, min = 32, max = 158),1],
       y = points_fechado_noite[find_day(day = 80, min = 32, max = 158),2],
       pch = 21, bg = "white", col = "#E69F00", lwd = 3, cex = 3.5)

text(x = points_fechado_noite[find_day(day = 80, min = 32, max = 158),1],
       y = points_fechado_noite[find_day(day = 80, min = 32, max = 158),2], labels = "80", cex = 0.7, font = 2, col = "#E69F00")

points(x = points_fechado_noite[find_day(day = 116, min = 32, max = 158),1],
       y = points_fechado_noite[find_day(day = 116, min = 32, max = 158),2],
       pch = 21, bg = "white", col = "#E69F00", lwd = 3, cex = 3.5)

text(x = points_fechado_noite[find_day(day = 116, min = 32, max = 158),1],
       y = points_fechado_noite[find_day(day = 116, min = 32, max = 158),2], labels = "116", cex = 0.7, font = 2, col = "#E69F00")

points(x = points_fechado_noite[find_day(day = 158, min = 32, max = 158),1],
       y = points_fechado_noite[find_day(day = 158, min = 32, max = 158),2],
       pch = 21, bg = "white", col = "#E69F00", lwd = 3, cex = 3.5)

text(x = points_fechado_noite[find_day(day = 158, min = 32, max = 158),1],
       y = points_fechado_noite[find_day(day = 158, min = 32, max = 158),2], labels = "158", cex = 0.7, font = 2, col = "#E69F00")
#################################################



########################## species_pred #################################


sp_names <- rownames(species_pred)
sp_names <- substr(sp_names, start = 1, stop = 3)


for(i in 1:nrow(species_pred)){
  #points(x = species_pred[i,1],
   #    y = species_pred[i,2],
    #   pch = 21, bg = "white", col = "grey50", lwd = 2, cex = 4)

text_contour(x = species_pred[i,1],
       y = species_pred[i,2], labels = sp_names[i], cex = 0.8, col = "white", thick = 0.004)
  
text(x = species_pred[i,1],
       y = species_pred[i,2], labels = sp_names[i], cex = 0.8, col = "grey30")
}




axis(1)
axis(2, cex.axis = 1, las = 2)

title(xlab = "nMDS 1", line = 3, cex.lab = 1.2)
title(ylab = "nMDS 2", line = 3, cex.lab = 1.2)

#letters(x = 10, y = 97, "b)", cex = 1.5)


#par(new = TRUE)
#plot(NA, xlim = c(0, 100), ylim = c(0, 100), xlab = "", ylab = "", xaxt = "n", yaxt = "n", bty = "n")

#legend(x = 100, y = 100, xjust = 1, yjust = 1, lty = c(1,1,1), lwd = 3, legend = c("Control", "Closed", "Late"), col = c("#009E73", "#56B4E9","#D55E00"), bty = "n")

#dev.off()


```


