---
title: "Supporting Information 5 - Analysis of the effect of environmental variability, community size, alpha and gamma diversity on community variability"
author: "Rodolfo Pelinson"
date: "2026-04-12"
output: github_document
editor_options: 
  chunk_output_type: console
---


## Loading packages and functions


```{r, warning=FALSE, echo = FALSE, include=FALSE}
dir<-("C:/Users/rodol/OneDrive/repos/PrioEff_TimeOfAssembly")
```

```{r, warning=FALSE, message = FALSE}

source(paste(sep = "/",dir,"functions/remove_sp.R"))
source(paste(sep = "/",dir,"functions/get_scaled_lvs.R"))
source(paste(sep = "/",dir,"functions/text_contour.R"))
source(paste(sep = "/",dir,"functions/letters.R"))

```

```{r, warning=FALSE, message = FALSE}

library(vegan)
library(gllvm)
library(mvabund)
library(DHARMa)
library(glmmTMB)
library(vioplot)
library(yarrr)
library(colorspace)
library(iNEXT)
library(iNEXT.beta3D)
library(iNEXT.3D)
library(shape)
library(car)

```


```{r}
sessionInfo()
```

## Loading and preparing data


```{r, message = FALSE, warning=FALSE}
source(paste(sep = "/",dir,"ajeitando_planilhas.R"))
beta_data <- read.csv(paste(sep = "/",dir,"data/beta_data.csv"))
```


```{r}

#Now excluding the late treatment because it complicate things
comm_all_2 <- comm_all[Exp_design_all$treatments != "atrasado",]
Exp_design_all_2 <- Exp_design_all[Exp_design_all$treatments != "atrasado",]

comm_all_2 <- remove_sp(comm_all_2, 0)

ncol(comm_all_2)


nrow(comm_all_2)
nrow(Exp_design_all_2)


ID <-  as.factor(Exp_design_all_2$sites)

AM_by_block <- interaction(as.factor(Exp_design_all_2$block), as.factor( Exp_design_all_2$AM))


Exp_design_all_2$AM <- as.factor(Exp_design_all_2$AM)
Exp_design_all_2$AM_numeric <- as.numeric(Exp_design_all_2$AM)
Exp_design_all_2$AM_numeric_quad <- Exp_design_all_2$AM_numeric^2


Exp_design_all_2$AM_days <- Exp_design_all_2$AM_numeric

Exp_design_all_2$AM_days[Exp_design_all_2$AM_numeric==1] <- 32
Exp_design_all_2$AM_days[Exp_design_all_2$AM_numeric==2] <- 80
Exp_design_all_2$AM_days[Exp_design_all_2$AM_numeric==3] <- 116
Exp_design_all_2$AM_days[Exp_design_all_2$AM_numeric==4] <- 158

Exp_design_all_2$AM_days_st <- scale(Exp_design_all_2$AM_days)
attr_AM_days <- attributes(Exp_design_all_2$AM_days_st)
Exp_design_all_2$AM_days_st <- Exp_design_all_2$AM_days_st[,1]

unscale <- function(x, atributes, reverse = FALSE){
  if(isTRUE(reverse)){
      x <- (x - atributes$`scaled:center`) / atributes$`scaled:scale` 
  }else{
      x <- (x * atributes$`scaled:scale`) + atributes$`scaled:center`
  }
  return(x)
}

Exp_design_all_2$AM_days_quad <- Exp_design_all_2$AM_days^2
Exp_design_all_2$AM_days_st_quad <- Exp_design_all_2$AM_days_st^2


```

# Effect of Time on tichness, community size and gamma diversity

### Richness

```{r}


richness <- rowSums(decostand(comm_all_2, method = "pa"))
#richness_null <- rowSums(decostand(null_com, method = "pa"))


mod_rich_null<- glmmTMB(richness ~ 1 + (1|block2/sites), data = Exp_design_all_2, family ="gaussian")
mod_rich_day <- glmmTMB(richness ~ AM_days_st + (1|block2/sites), data = Exp_design_all_2, family ="gaussian")
mod_rich_day_quad <- glmmTMB(richness ~ AM_days_st_quad + AM_days_quad + (1|block2/sites), data = Exp_design_all_2, family ="gaussian")

anova_rich <- anova(mod_rich_null, mod_rich_day, mod_rich_day_quad)
plot(simulateResiduals(mod_rich_day_quad))
anova_rich

```


### Community size

```{r}

abundance <- rowSums(comm_all_2)

#abundance_10 <- abundance/10

mod_abundance_null<- glmmTMB(abundance ~ 1 + (1|block2/sites), data = Exp_design_all_2, family ="nbinom2")
mod_abundance_day <- glmmTMB(abundance ~ AM_days_st + (1|block2/sites), data = Exp_design_all_2, family ="nbinom2", control=glmmTMBControl(optimizer=optim,
               optArgs=list(method="BFGS")))
mod_abundance_day_quad <- glmmTMB(abundance ~ AM_days_st + AM_days_st_quad + (1|block2/sites), data = Exp_design_all_2, family ="nbinom2")
plot(simulateResiduals(mod_abundance_day_quad))

anova_abundance <- anova(mod_abundance_null, mod_abundance_day, mod_abundance_day_quad)

anova_abundance


new_data_days <- data.frame(AM_days_st = seq(from = min(Exp_design_all_2$AM_days_st), to = max(Exp_design_all_2$AM_days_st), length.out = 100),
                            AM_days_st_quad = seq(from = min(Exp_design_all_2$AM_days_st), to = max(Exp_design_all_2$AM_days_st), length.out = 100)^2)

predicted_ab_quad <- predict(mod_abundance_day_quad, newdata = new_data_days, se.fit = TRUE, re.form = NA)
predicted_ab_quad$upper <- exp(predicted_ab_quad$fit + predicted_ab_quad$se.fit * qnorm(0.975))
predicted_ab_quad$lower <- exp(predicted_ab_quad$fit + predicted_ab_quad$se.fit * qnorm(0.025)) 
predicted_ab_quad$fit <- exp(predicted_ab_quad$fit)


```



### Gamma diversity

```{r, cache = TRUE}
#Gama
gamma <- aggregate(comm_all_2, by = list(Exp_design_all_2$AM), FUN = sum)

rownames(gamma) <- gamma[,1]
gamma <- gamma[,-1]

comm_AM1 <- comm_all_2[Exp_design_all_2$AM == 1,]
comm_AM2 <- comm_all_2[Exp_design_all_2$AM == 2,]
comm_AM3 <- comm_all_2[Exp_design_all_2$AM == 3,]
comm_AM4 <- comm_all_2[Exp_design_all_2$AM == 4,]

comm_AM1 <- remove_sp(comm_AM1, 0)
comm_AM2 <- remove_sp(comm_AM2, 0)
comm_AM3 <- remove_sp(comm_AM3, 0)
comm_AM4 <- remove_sp(comm_AM4, 0)

rownames(comm_AM1) <- Exp_design$sites[Exp_design$treatments != "atrasado"]
rownames(comm_AM2) <- Exp_design$sites[Exp_design$treatments != "atrasado"]
rownames(comm_AM3) <- Exp_design$sites[Exp_design$treatments != "atrasado"]
rownames(comm_AM4) <- Exp_design$sites[Exp_design$treatments != "atrasado"]

com_tempos <- list(t(comm_AM1), t(comm_AM2), t(comm_AM3), t(comm_AM4))

inext_coverage_0 <- iNEXTbeta3D(com_tempos, datatype = "abundance", q = 0, diversity = "TD",   base = "coverage")
inext_coverage_0$Dataset_1$gamma
inext_coverage_0$Dataset_2$gamma
inext_coverage_0$Dataset_3$gamma
inext_coverage_0$Dataset_4$gamma

inext_coverage_0$Dataset_1$alpha
inext_coverage_0$Dataset_2$alpha
inext_coverage_0$Dataset_3$alpha
inext_coverage_0$Dataset_4$alpha


inext_coverage_2 <- iNEXTbeta3D(com_tempos, datatype = "abundance", q = 2, diversity = "TD",   base = "coverage")
inext_coverage_2$Dataset_1$gamma
inext_coverage_2$Dataset_2$gamma
inext_coverage_2$Dataset_3$gamma
inext_coverage_2$Dataset_4$gamma

inext_coverage_4 <- iNEXTbeta3D(com_tempos, datatype = "abundance", q = 4, diversity = "TD",   base = "coverage")
inext_coverage_4$Dataset_1$gamma
inext_coverage_4$Dataset_2$gamma
inext_coverage_4$Dataset_3$gamma
inext_coverage_4$Dataset_4$gamma

inext_coverage_estimated_0 <- iNEXTbeta3D(com_tempos, datatype = "abundance", q = 0, diversity = "TD",   base = "coverage", level = 0.997, nboot = 100)
inext_coverage_estimated_0$Dataset_1$gamma
inext_coverage_estimated_0$Dataset_2$gamma
inext_coverage_estimated_0$Dataset_3$gamma
inext_coverage_estimated_0$Dataset_4$gamma

inext_coverage_estimated_0$Dataset_1$alpha
inext_coverage_estimated_0$Dataset_2$alpha
inext_coverage_estimated_0$Dataset_3$alpha
inext_coverage_estimated_0$Dataset_4$alpha


inext_coverage_estimated_2 <- iNEXTbeta3D(com_tempos, datatype = "abundance", q = 2, diversity = "TD",   base = "coverage", level = 0.997, nboot = 100)
inext_coverage_estimated_2$Dataset_1$gamma
inext_coverage_estimated_2$Dataset_2$gamma
inext_coverage_estimated_2$Dataset_3$gamma
inext_coverage_estimated_2$Dataset_4$gamma

inext_coverage_estimated_2$Dataset_1$alpha
inext_coverage_estimated_2$Dataset_2$alpha
inext_coverage_estimated_2$Dataset_3$alpha
inext_coverage_estimated_2$Dataset_4$alpha

#inext_estimate <- estimate3D(com_tempos, datatype = "abundance", base = "coverage", level = 0.999, diversity = "TD")


```


### Plots

```{r,   fig.width = 3, fig.height = 8, dpi = 600, dev.args= list(pointsize=12)}

#pdf("Plots/Community structure analysis/size_alfa_gama.pdf", width = 3, height = 8, pointsize = 12)

#predicted_dev <- predict(mod_dev_am_num, newdata = new_data, se.fit = TRUE, re.form = NA)
#predicted_dev$upper <- predicted_dev$fit + predicted_dev$se.fit * 1.96
#predicted_dev$lower <- predicted_dev$fit- predicted_dev$se.fit * 1.96 
par(mfrow = c(3,1), xpd = NA)

par(mar  = c(4,5,1,1), bty = "l")
plot(abundance ~ jitter(AM_days_st, 1),
     data = Exp_design_all_2, xaxt = "n", ylab = "", xlab = "", type = "n",  xlim = unscale(x = c(20,170), atributes = attr_AM_days, reverse = TRUE), xaxs = "i" )#, ylim = c(-3,5),)

polygon(x = c(new_data_days$AM_days_st[1:100], new_data_days$AM_days_st[100:1]),
        y = c(predicted_ab_quad$upper[1:100], predicted_ab_quad$lower[100:1]), col = transparent("grey50", trans.val = 0.5), border = FALSE) 

points(abundance ~ jitter(AM_days_st, 1), pch = 21, col= "black",bg = transparent("orchid3", trans.val = 0.5), cex = 1.25, data = Exp_design_all_2)
lines(x = new_data_days$AM_days_st,y = predicted_ab_quad$fit, col = "black", lwd = 2)
title(ylab = "Total abundance", cex.lab = 1.25, line= 2.25)
axis(1, at = unscale(x = c(32,80,116,158), atributes = attr_AM_days, reverse = TRUE), labels = c("32", "80", "116", "158"))
title(xlab = "Days", cex.lab = 1.25 ,line = 2.25)

letters(x = 5, y = 97, "a)", cex = 1.5)



par(mar  = c(4,5,1,1), bty = "l")
plot(richness ~ jitter(AM_days_st, 1),
     data = Exp_design_all_2, xaxt = "n", ylab = "", xlab = "", type = "n"
     ,  xlim = unscale(x = c(20,170), atributes = attr_AM_days, reverse = TRUE), xaxs = "i", ylim = c(0, 10))#, ylim = c(-3,5),)

#polygon(x = c(new_data$AM_numeric[1:100], new_data$AM_numeric[100:1]),
#        y = c(predicted_dev$upper[1:100], predicted_dev$lower[100:1]), col = transparent("grey50", trans.val = 0.5), border = FALSE) 

points(richness ~ jitter(AM_days_st, 1), pch = 21, col= "black",bg = transparent("darkgoldenrod3", trans.val = 0.5), cex = 1.25, data = Exp_design_all_2)
#lines(x = new_data$AM_numeric,y = predicted_dev$fit, col = "black", lwd = 2)
title(ylab = "Alpha diversity", cex.lab = 1.25, line= 2.25)
axis(1, at = unscale(x = c(32,80,116,158), atributes = attr_AM_days, reverse = TRUE), labels = c("32", "80", "116", "158"))
title(xlab = "Days", cex.lab = 1.25 ,line = 2.25)

letters(x = 5, y = 97, "b)", cex = 1.5)






par(mar  = c(4,5,1,1), bty = "l")
plot(NA, ylim = c(8,35), xlim = c(20,170), xaxt = "n",  ylab = "", xlab = "")
Arrows(x0 = c(32,80,116,158),
       x1 = c(32,80,116,158),
       y0 = c(inext_coverage_estimated_0$Dataset_1$gamma$LCL,
              inext_coverage_estimated_0$Dataset_2$gamma$LCL,
              inext_coverage_estimated_0$Dataset_3$gamma$LCL,
              inext_coverage_estimated_0$Dataset_4$gamma$LCL),
       y1 = c(inext_coverage_estimated_0$Dataset_1$gamma$UCL,
              inext_coverage_estimated_0$Dataset_2$gamma$UCL,
              inext_coverage_estimated_0$Dataset_3$gamma$UCL,
              inext_coverage_estimated_0$Dataset_4$gamma$UCL),
       arr.type = "T", code = 3, lwd = 2, col = "grey40")
points(x = c(32,80,116,158), y = c(inext_coverage_estimated_0$Dataset_1$gamma$Gamma,
                                   inext_coverage_estimated_0$Dataset_2$gamma$Gamma,
                                   inext_coverage_estimated_0$Dataset_3$gamma$Gamma,
                                   inext_coverage_estimated_0$Dataset_4$gamma$Gamma), pch = 16, cex = 2)

title(ylab = "Gamma diversity", cex.lab = 1.25, line= 2.25)
axis(1, at = c(32,80,116,158), labels = c("32", "80", "116", "158"))

title(xlab = "Days", cex.lab = 1.25 ,line = 2.25)
letters(x = 5, y = 97, "c)", cex = 1.5)

#dev.off()

```





# Effect of community size, alpha and gamma diversity on observed and expected beta-diversity

```{r}
beta_data$alpha <- richness
beta_data$size <- abundance

gamma <- c(rep(inext_coverage_estimated_0$Dataset_1$gamma$Gamma, length(unique(beta_data$sites))),
rep(inext_coverage_estimated_0$Dataset_2$gamma$Gamma, length(unique(beta_data$sites))),
rep(inext_coverage_estimated_0$Dataset_3$gamma$Gamma, length(unique(beta_data$sites))),
rep(inext_coverage_estimated_0$Dataset_4$gamma$Gamma, length(unique(beta_data$sites))))

beta_data$gamma <- gamma

beta_data$size <- scale(beta_data$size)
beta_data$alpha <- scale(beta_data$alpha)
beta_data$gamma <- scale(beta_data$gamma)

```

### Models
```{r}

cor(beta_data[,colnames(beta_data) %in% c("alpha","size","gamma")])

mod_obs_beta <- glmmTMB(observed_distances ~ alpha + size + gamma + (1|block2/sites), data = beta_data, family = gaussian(link = "identity"), control=glmmTMBControl(optimizer=optim, optArgs=list(method="BFGS")))
plot(simulateResiduals(mod_obs_beta))
Anova(mod_obs_beta)


mod_exp_beta <- glmmTMB(expected_distances ~ alpha + size + gamma + (1|block2/sites), data = beta_data, family = gaussian(link = "identity"))
plot(simulateResiduals(mod_exp_beta))
Anova(mod_exp_beta)


mod_dev_beta <- glmmTMB(deviation_distances ~ alpha + size + gamma + (1|block2/sites), data = beta_data, family = gaussian(link = "identity"))
plot(simulateResiduals(mod_dev_beta))
Anova(mod_dev_beta)


```


### Plots


```{r}
newdata_alpha <- data.frame(alpha = seq(from = min(beta_data$alpha), to = max(beta_data$alpha), length.out = 100),
                            size = rep(mean(beta_data$size), 100),
                            gamma = rep(mean(beta_data$gamma), 100))

newdata_size <- data.frame(alpha = rep(mean(beta_data$alpha), 100),
                            size = seq(from = min(beta_data$size), to = max(beta_data$size), length.out = 100),
                            gamma = rep(mean(beta_data$gamma), 100))


predicted_obs_alpha <- predict(mod_obs_beta, newdata = newdata_alpha, se.fit = TRUE, re.form = NA)
predicted_obs_alpha$upper <- predicted_obs_alpha$fit + predicted_obs_alpha$se.fit * qnorm(0.975)
predicted_obs_alpha$lower <- predicted_obs_alpha$fit + predicted_obs_alpha$se.fit * qnorm(0.025)
predicted_obs_alpha$fit <- predicted_obs_alpha$fit

predicted_exp_alpha <- predict(mod_exp_beta, newdata = newdata_alpha, se.fit = TRUE, re.form = NA)
predicted_exp_alpha$upper <- predicted_exp_alpha$fit + predicted_exp_alpha$se.fit * qnorm(0.975)
predicted_exp_alpha$lower <- predicted_exp_alpha$fit + predicted_exp_alpha$se.fit * qnorm(0.025)
predicted_exp_alpha$fit <- predicted_exp_alpha$fit



predicted_obs_size <- predict(mod_obs_beta, newdata = newdata_size, se.fit = TRUE, re.form = NA)
predicted_obs_size$upper <- predicted_obs_size$fit + predicted_obs_size$se.fit * qnorm(0.975)
predicted_obs_size$lower <- predicted_obs_size$fit + predicted_obs_size$se.fit * qnorm(0.025)
predicted_obs_size$fit <- predicted_obs_size$fit

predicted_exp_size <- predict(mod_exp_beta, newdata = newdata_size, se.fit = TRUE, re.form = NA)
predicted_exp_size$upper <- predicted_exp_size$fit + predicted_exp_size$se.fit * qnorm(0.975)
predicted_exp_size$lower <- predicted_exp_size$fit + predicted_exp_size$se.fit * qnorm(0.025)
predicted_exp_size$fit <- predicted_exp_size$fit



```



```{r,   fig.width = 6, fig.height = 6, dpi = 600, dev.args= list(pointsize=10)}
set.seed(1)
#svg(file = "plots/Community structure analysis/beta_dataiation.svg", width = 6, height = 3, pointsize = 8)

par(mfrow = c(2,2))

#####################################################################################################################


par(mar  = c(4,4,1,1), bty = "l", new = FALSE)
plot(observed_distances ~ alpha,
     data = beta_data, xaxt = "n", ylab = "", xlab = "", type = "n")

polygon(x = c(newdata_alpha$alpha[1:100], newdata_alpha$alpha[100:1]),
        y = c(predicted_obs_alpha$upper[1:100], predicted_obs_alpha$lower[100:1]), col = transparent("black", trans.val = 0.6), border = FALSE) 

lines(x = newdata_alpha$alpha,y = predicted_obs_alpha$fit, col = "black", lwd = 2)

points(observed_distances ~ alpha, pch = 21, col= "black",bg = transparent("black", trans.val = 0.6), cex = 1.1, data = beta_data)

title(ylab = "Observed distances", cex.lab = 1.25, line= 2.25)
axis(1)
title(xlab = "Alpha diversity (scaled)", cex.lab = 1.25 ,line = 2.25)


letters(x = 5, y = 97, "a)", cex = 1.5)




par(mar  = c(4,4,1,1), bty = "l", new = FALSE)
plot(expected_distances ~ alpha,
     data = beta_data, xaxt = "n", ylab = "", xlab = "", type = "n")

polygon(x = c(newdata_alpha$alpha[1:100], newdata_alpha$alpha[100:1]),
        y = c(predicted_exp_alpha$upper[1:100], predicted_exp_alpha$lower[100:1]), col = transparent("black", trans.val = 0.6), border = FALSE) 

lines(x = newdata_alpha$alpha,y = predicted_exp_alpha$fit, col = "black", lwd = 2)

points(expected_distances ~ alpha, pch = 21, col= "black",bg = transparent("black", trans.val = 0.6), cex = 1.1, data = beta_data)

title(ylab = "Expected distances", cex.lab = 1.25, line= 2.25)
axis(1)
title(xlab = "Alpha diversity (scaled)", cex.lab = 1.25 ,line = 2.25)


letters(x = 5, y = 97, "b)", cex = 1.5)



par(mar  = c(4,4,1,1), bty = "l", new = FALSE)
plot(observed_distances ~ size,
     data = beta_data, xaxt = "n", ylab = "", xlab = "", type = "n")

polygon(x = c(newdata_size$size[1:100], newdata_size$size[100:1]),
        y = c(predicted_obs_size$upper[1:100], predicted_obs_size$lower[100:1]), col = transparent("black", trans.val = 0.6), border = FALSE) 

lines(x = newdata_size$size,y = predicted_obs_size$fit, col = "black", lwd = 2)

points(observed_distances ~ size, pch = 21, col= "black",bg = transparent("black", trans.val = 0.6), cex = 1.1, data = beta_data)

title(ylab = "Observed distances", cex.lab = 1.25, line= 2.25)
axis(1)
title(xlab = "Community size (scaled)", cex.lab = 1.25 ,line = 2.25)


letters(x = 5, y = 97, "c)", cex = 1.5)




par(mar  = c(4,4,1,1), bty = "l", new = FALSE)
plot(expected_distances ~ size,
     data = beta_data, xaxt = "n", ylab = "", xlab = "", type = "n")

polygon(x = c(newdata_size$size[1:100], newdata_size$size[100:1]),
        y = c(predicted_exp_size$upper[1:100], predicted_exp_size$lower[100:1]), col = transparent("black", trans.val = 0.6), border = FALSE) 

lines(x = newdata_size$size,y = predicted_exp_size$fit, col = "black", lwd = 2)

points(expected_distances ~ size, pch = 21, col= "black",bg = transparent("black", trans.val = 0.6), cex = 1.1, data = beta_data)

title(ylab = "Expected distances", cex.lab = 1.25, line= 2.25)
axis(1)
title(xlab = "Community size (scaled)", cex.lab = 1.25 ,line = 2.25)


letters(x = 5, y = 97, "d)", cex = 1.5)



#dev.off()
```











# Environmental variability
Preparing data

```{r}

Env$AM_match <- rep(NA, nrow(Env))

Env$AM_match[Env$amostragem == 2] <- 1
Env$AM_match[Env$amostragem == 5] <- 2
Env$AM_match[Env$amostragem == 7] <- 3
Env$AM_match[Env$amostragem == 9] <- 4

Env <- Env[is.na(Env$AM_match)==FALSE,]


```

Replace temperature information with the HOBOs temperature information, which is much more accurate
```{r}

hobo_env <- read.csv(paste(sep = "/",dir,"data/hobo_env.csv"))

index_env <- interaction(Env$id, Env$AM_match)
index_hobo <- interaction(hobo_env$ID, hobo_env$AM)

index <- match(index_env, index_hobo)
hobo_env <- hobo_env[index,]

#data.frame(Env$id, hobo_env$ID, Env$AM_match, hobo_env$AM)

Env$hobo_temp <- hobo_env$temp_mean
Env$iluminance <- hobo_env$light_mean


Env <- Env[,-which(colnames(Env) == "Temperatura")]
```


```{r}

Exp_design_all_2$site_AM <- interaction(Exp_design_all_2$sites, Exp_design_all_2$AM)
Env$site_AM <- interaction(Env$id, Env$AM_match)


Env_2 <- Env[Env$Tratamento != "atrasado",]
Env_2 <- Env_2[match(Exp_design_all_2$site_AM, Env_2$site_AM),]

nrow(Env_2)
nrow(Exp_design_all_2)
```



Environmental variability
```{r}


only_Env <- Env_2[,colnames(Env_2) %in% c("pH","OD","Condutividade","TDS","hobo_temp","iluminance")]

only_Env_st <- decostand(only_Env, method = "stand")

dist_env <- vegdist(only_Env_st, method = "euclidean")

env_var <- betadisper(dist_env, group = Env_2$AM_match)
```



PCA
```{r}
pca_env <- rda(only_Env_st)

env_eigenvalues <- pca_env$CA$eig / sum(pca_env$CA$eig)
env_eigenvalues

env_PCs <- pca_env$CA$u

pca_env$CA$v
```


First PC is basically related to conductivity, total dissolved solids and temperature
Second PC is basically related to pH
Third PC is basically related to dissolved oxygen


## Test of environmental effect on community variability

Effect of environmental variability on observed community variability
```{r,   fig.width = 6, fig.height = 3, dpi = 600, dev.args= list(pointsize=8)}
Exp_design_all_2$env_var <- env_var$distances

mod_obs_am_num_env <- glmmTMB(beta_data$observed_distances ~ AM_days_st + env_var + (1|block2/sites), data = Exp_design_all_2, control = glmmTMBControl(optimizer=optim, optArgs=list(method="BFGS")))
plot(simulateResiduals(mod_obs_am_num_env))
Anova(mod_obs_am_num_env)





```


Effect of environmental predictors on observed community variability
```{r}
mod_obs_env_pcs <- glmmTMB(beta_data$observed_distances ~ AM_days_st + (1|block2/sites) + 
                            env_PCs[,1] +
                            env_PCs[,2] + 
                            env_PCs[,3], data = Exp_design_all_2, control = glmmTMBControl(optimizer=optim, optArgs=list(method="BFGS")))
Anova(mod_obs_env_pcs)
```



Effect of environmental variability on beta deviation
```{r,   fig.width = 6, fig.height = 3, dpi = 600, dev.args= list(pointsize=8)}
Exp_design_all_2$env_var <- env_var$distances

mod_dev_am_num_env <- glmmTMB(beta_data$deviation_distances ~ AM_days_st + env_var + (1|block2/sites), data = Exp_design_all_2, control = glmmTMBControl(optimizer=optim, optArgs=list(method="BFGS")))
plot(simulateResiduals(mod_dev_am_num_env))
Anova(mod_dev_am_num_env)

```

Effect of environmental predictors on beta deviation
```{r,   fig.width = 6, fig.height = 3, dpi = 600, dev.args= list(pointsize=8)}
mod_dev_env_pcs <- glmmTMB(beta_data$deviation_distances ~ AM_days_st + (1|block2/sites) + 
                            env_PCs[,1] +
                            env_PCs[,2] + 
                            env_PCs[,3], data = Exp_design_all_2, control = glmmTMBControl(optimizer=optim, optArgs=list(method="BFGS")))
plot(simulateResiduals(mod_dev_env_pcs))
Anova(mod_dev_env_pcs)
```


## Test of the effect of time om environmental parameters


Effect of time on environmental variability
```{r,   fig.width = 6, fig.height = 3, dpi = 600, dev.args= list(pointsize=8)}

env_var <- env_var$distances

mod_env_null <- glmmTMB(env_var ~ 1 + (1|block2/sites), data = Exp_design_all_2, control = glmmTMBControl(optimizer=optim, optArgs=list(method="BFGS")))

mod_env_am_num <- glmmTMB(env_var ~ AM_days_st + (1|block2/sites), data = Exp_design_all_2, control = glmmTMBControl(optimizer=optim, optArgs=list(method="BFGS")))

mod_env_am_num_quad <- glmmTMB(env_var ~ AM_days_st + AM_days_st_quad + (1|block2/sites), data = Exp_design_all_2)

plot(simulateResiduals(mod_env_am_num_quad))

anova_env <- anova(mod_env_null, mod_env_am_num, mod_env_am_num_quad)
anova_env

```


Now environmental PCs
```{r,   fig.width = 6, fig.height = 3, dpi = 600, dev.args= list(pointsize=8)}

mod_env1_pcs_null <- glmmTMB(env_PCs[,1] ~ 1 + (1|block2/sites), data = Exp_design_all_2)
mod_env1_pcs_lin <- glmmTMB(env_PCs[,1] ~ AM_days_st + (1|block2/sites), data = Exp_design_all_2)
mod_env1_pcs_quad <- glmmTMB(env_PCs[,1] ~ AM_days_st + AM_days_st_quad + (1|block2/sites), data = Exp_design_all_2)

plot(simulateResiduals(mod_env1_pcs_quad))

anova(mod_env1_pcs_null, mod_env1_pcs_lin, mod_env1_pcs_quad)
```

```{r,   fig.width = 6, fig.height = 3, dpi = 600, dev.args= list(pointsize=8)}

Exp_design_all_2$AM_days_st_third <- Exp_design_all_2$AM_days_st^3

mod_env2_pcs_null <- glmmTMB(env_PCs[,2] ~ 1 + (1|block2/sites), data = Exp_design_all_2)
mod_env2_pcs_lin <- glmmTMB(env_PCs[,2] ~ AM_days_st + (1|block2/sites), data = Exp_design_all_2)
mod_env2_pcs_quad <- glmmTMB(env_PCs[,2] ~ AM_days_st + AM_days_st_quad + (1|block2/sites), data = Exp_design_all_2)
mod_env2_pcs_third <- glmmTMB(env_PCs[,2] ~ AM_days_st + AM_days_st_quad + AM_days_st_third + (1|block2/sites), data = Exp_design_all_2)

plot(simulateResiduals(mod_env2_pcs_third))

anova(mod_env2_pcs_null, mod_env2_pcs_lin, mod_env2_pcs_quad,mod_env2_pcs_third)
```

```{r,   fig.width = 6, fig.height = 3, dpi = 600, dev.args= list(pointsize=8)}
mod_env3_pcs_null <- glmmTMB(env_PCs[,3] ~ 1 + (1|block2/sites), data = Exp_design_all_2)
mod_env3_pcs_lin <- glmmTMB(env_PCs[,3] ~ AM_days_st + (1|block2/sites), data = Exp_design_all_2)
mod_env3_pcs_quad <- glmmTMB(env_PCs[,3] ~ AM_days_st + AM_days_st_quad + (1|block2/sites), data = Exp_design_all_2)

plot(simulateResiduals(mod_env3_pcs_quad))


anova(mod_env3_pcs_null, mod_env3_pcs_lin, mod_env3_pcs_quad)
```


## Test of the effect environmental parameters (without the effects of time) on community variability

Basically all environmental predictors vary throughout time. We took the residual of such models e checked if those residuals can explain community variability alongside with time.

```{r,   fig.width = 6, fig.height = 3, dpi = 600, dev.args= list(pointsize=8)}
Exp_design_all_2$resid_PC1 <- residuals(mod_env1_pcs_quad)
Exp_design_all_2$resid_PC2 <- residuals(mod_env2_pcs_third)
Exp_design_all_2$resid_PC3 <- residuals(mod_env3_pcs_quad)


mod_obs_env_pcs <- glmmTMB(beta_data$observed_distances ~ (1|block2/sites) + AM_days_st +
                            resid_PC1 +
                            resid_PC2 + 
                            resid_PC3, data = Exp_design_all_2, control = glmmTMBControl(optimizer=optim, optArgs=list(method="BFGS")))
plot(simulateResiduals(mod_obs_env_pcs))

Anova(mod_obs_env_pcs)


mod_dev_env_pcs <- glmmTMB(beta_data$deviation_distances ~ (1|block2/sites) + AM_days_st +
                            resid_PC1 +
                            resid_PC2 + 
                            resid_PC3, data = Exp_design_all_2)
plot(simulateResiduals(mod_dev_env_pcs))
Anova(mod_dev_env_pcs)
```




### Making predictons

```{r}
new_data_days$AM_days_st_third <- new_data_days$AM_days_st^3

predicted_env_PC1_time <- predict(mod_env1_pcs_quad, newdata = new_data_days, se.fit = TRUE, re.form = NA)
predicted_env_PC1_time$upper <- predicted_env_PC1_time$fit + predicted_env_PC1_time$se.fit * qnorm(0.975)
predicted_env_PC1_time$lower <- predicted_env_PC1_time$fit + predicted_env_PC1_time$se.fit * qnorm(0.025) 

predicted_env_PC2_time <- predict(mod_env2_pcs_third, newdata = new_data_days, se.fit = TRUE, re.form = NA)
predicted_env_PC2_time$upper <- predicted_env_PC2_time$fit + predicted_env_PC2_time$se.fit * qnorm(0.975)
predicted_env_PC2_time$lower <- predicted_env_PC2_time$fit + predicted_env_PC2_time$se.fit * qnorm(0.025) 

predicted_env_PC3_time <- predict(mod_env3_pcs_quad, newdata = new_data_days, se.fit = TRUE, re.form = NA)
predicted_env_PC3_time$upper <- predicted_env_PC3_time$fit + predicted_env_PC3_time$se.fit * qnorm(0.975)
predicted_env_PC3_time$lower <- predicted_env_PC3_time$fit + predicted_env_PC3_time$se.fit * qnorm(0.025) 



new_data_obs_PC3 <- new_data_days
new_data_obs_PC3$resid_PC3 <- seq(from = min(Exp_design_all_2$resid_PC3), to = max(Exp_design_all_2$resid_PC3), length.out = nrow(new_data_obs_PC3))
new_data_obs_PC3$resid_PC2 <- rep(median(Exp_design_all_2$resid_PC2), nrow(new_data_obs_PC3))
new_data_obs_PC3$resid_PC1 <- rep(median(Exp_design_all_2$resid_PC1), nrow(new_data_obs_PC3))
new_data_obs_PC3$AM_days_st <- rep(median(new_data_obs_PC3$AM_days_st), nrow(new_data_obs_PC3))
new_data_obs_PC3$AM_days_st_quad <- new_data_obs_PC3$AM_days_st^2


predicted_obs_PC3 <- predict(mod_obs_env_pcs, newdata = new_data_obs_PC3, se.fit =  TRUE, re.form = NA)
predicted_obs_PC3$upper <- predicted_obs_PC3$fit + predicted_obs_PC3$se.fit * qnorm(0.975)
predicted_obs_PC3$lower <- predicted_obs_PC3$fit + predicted_obs_PC3$se.fit * qnorm(0.025) 

predicted_dev_PC3 <- predict(mod_dev_env_pcs, newdata = new_data_obs_PC3, se.fit =  TRUE, re.form = NA)
predicted_dev_PC3$upper <- predicted_dev_PC3$fit + predicted_dev_PC3$se.fit * qnorm(0.975)
predicted_dev_PC3$lower <- predicted_dev_PC3$fit + predicted_dev_PC3$se.fit * qnorm(0.025) 

```






### Plots

#### Environmental variability VS community variability
```{r,   fig.width = 6, fig.height = 3, dpi = 600, dev.args= list(pointsize=8)}
set.seed(1)
#svg(file = "plots/Community structure analysis/beta_dataiation.svg", width = 6, height = 3, pointsize = 8)

par(mfrow = c(1,2))

par(mar  = c(4,4,1,1), bty = "l", new = FALSE)
plot(beta_data$observed_distances ~ env_var,
     data = Exp_design_all_2, xaxt = "n", ylab = "", xlab = "", type = "n")


points(beta_data$observed_distances[Exp_design_all_2$AM == 1] ~ env_var, pch = 21, col= "black",bg = transparent("grey80", trans.val = 0.6), cex = 1.1, data = Exp_design_all_2[Exp_design_all_2$AM == 1,])

points(beta_data$observed_distances[Exp_design_all_2$AM == 2] ~ env_var, pch = 21, col= "black",bg = transparent("grey50", trans.val = 0.6), cex = 1.1, data = Exp_design_all_2[Exp_design_all_2$AM == 2,])

points(beta_data$observed_distances[Exp_design_all_2$AM == 3] ~ env_var, pch = 21, col= "black",bg = transparent("grey20", trans.val = 0.6), cex = 1.1, data = Exp_design_all_2[Exp_design_all_2$AM == 3,])

points(beta_data$observed_distances[Exp_design_all_2$AM == 4] ~ env_var, pch = 21, col= "black",bg = transparent("black", trans.val = 0.6), cex = 1.1, data = Exp_design_all_2[Exp_design_all_2$AM == 4,])

title(ylab = "Observed community variability", cex.lab = 1.25, line= 2.25)
axis(1)
title(xlab = "Environmental variability", cex.lab = 1.25 ,line = 2.25)

par(new = TRUE, mar = c(0,0,0,0), bty = "n")
plot(NA, ylim = c(0,100), xlim = c(0,100), xaxt = "n", yaxt = "n")

legend(legend = c("32 days",
                  "80 days",
                  "116 days",
                  "158 days"), x = 100, y = 100, bty = "n", pch = 21, col = "black", pt.bg = c(transparent("grey80", trans.val = 0.6),
                                                                                              transparent("grey50", trans.val = 0.6),
                                                                                              transparent("grey20", trans.val = 0.6),
                                                                                              transparent("black", trans.val = 0.6)), xjust = 1, yjust = 1)

letters(x = 5, y = 97, "a)", cex = 1.5)

#####################################################################################################################


par(mar  = c(4,4,1,1), bty = "l", new = FALSE)
plot(beta_data$deviation_distances ~ env_var,
     data = Exp_design_all_2, xaxt = "n", ylab = "", xlab = "", type = "n")


points(beta_data$deviation_distances[Exp_design_all_2$AM == 1] ~ env_var, pch = 21, col= "black",bg = transparent("grey80", trans.val = 0.6), cex = 1.1, data = Exp_design_all_2[Exp_design_all_2$AM == 1,])

points(beta_data$deviation_distances[Exp_design_all_2$AM == 2] ~ env_var, pch = 21, col= "black",bg = transparent("grey50", trans.val = 0.6), cex = 1.1, data = Exp_design_all_2[Exp_design_all_2$AM == 2,])

points(beta_data$deviation_distances[Exp_design_all_2$AM == 3] ~ env_var, pch = 21, col= "black",bg = transparent("grey20", trans.val = 0.6), cex = 1.1, data = Exp_design_all_2[Exp_design_all_2$AM == 3,])

points(beta_data$deviation_distances[Exp_design_all_2$AM == 4] ~ env_var, pch = 21, col= "black",bg = transparent("black", trans.val = 0.6), cex = 1.1, data = Exp_design_all_2[Exp_design_all_2$AM == 4,])

title(ylab = "Beta deviation", cex.lab = 1.25, line= 2.25)
axis(1)
title(xlab = "Environmental variability", cex.lab = 1.25 ,line = 2.25)


letters(x = 5, y = 97, "b)", cex = 1.5)

#dev.off()
```



#### Environmental parameters VS time

```{r,   fig.width = 2, fig.height = 5, dpi = 600, dev.args= list(pointsize=8)}
set.seed(1)
#svg(file = "plots/Community structure analysis/beta_dataiation.svg", width = 6, height = 3, pointsize = 8)

par(mfrow = c(3,1))

unique_AM_days_st <- unique(Exp_design_all_2$AM_days_st)
unique_AM_days_st_orig <- unique(Exp_design_all_2$AM_days_st_orig)


par(mar  = c(4,5,1,1), bty = "l", new = FALSE)
plot(env_PCs[,1] ~ jitter(AM_days_st, 1),
     data = Exp_design_all_2, xaxt = "n", ylab = "", xlab = "", type = "n", xlim = c(min(unique_AM_days_st)*1.25,max(unique_AM_days_st)*1.25),  xaxs = "i")

polygon(x = c(new_data_days$AM_days_st[1:100], new_data_days$AM_days_st[100:1]),
        y = c(predicted_env_PC1_time$upper[1:100], predicted_env_PC1_time$lower[100:1]), col = transparent("blue", trans.val = 0.6), border = FALSE) 

points(env_PCs[,1] ~ jitter(AM_days_st, 0.5), pch = 21, col= "black",bg = transparent("blue", trans.val = 0.75), cex = 1.1, data = Exp_design_all_2)

lines(x = new_data_days$AM_days_st,y = predicted_env_PC1_time$fit, col = "black", lwd = 2)

title(ylab = "Environment PC1", cex.lab = 1, line= 4)
title(ylab = "(mostly Conductivity, total", cex.lab = 1, line= 3)
title(ylab = "dissolved solids and temperature)", cex.lab = 1, line= 2)

axis(1, at = unique_AM_days_st, labels = c("32", "80", "116", "158"))
title(xlab = "Days", cex.lab = 1.25 ,line = 2.25)

letters(x = 5, y = 97, "a)", cex = 1.5)

##############################################################################################



par(mar  = c(4,5,1,1), bty = "l", new = FALSE)
plot(env_PCs[,2] ~ jitter(AM_days_st, 1),
     data = Exp_design_all_2, xaxt = "n", ylab = "", xlab = "", type = "n", xlim = c(min(unique_AM_days_st)*1.25,max(unique_AM_days_st)*1.25),  xaxs = "i")

polygon(x = c(new_data_days$AM_days_st[1:100], new_data_days$AM_days_st[100:1]),
        y = c(predicted_env_PC2_time$upper[1:100], predicted_env_PC2_time$lower[100:1]), col = transparent("blue", trans.val = 0.6), border = FALSE) 

points(env_PCs[,2] ~ jitter(AM_days_st, 0.5), pch = 21, col= "black",bg = transparent("blue", trans.val = 0.75), cex = 1.1, data = Exp_design_all_2)

lines(x = new_data_days$AM_days_st,y = predicted_env_PC2_time$fit, col = "black", lwd = 2)

title(ylab = "Environment PC2", cex.lab = 1, line= 3)
title(ylab = "(mostly pH)", cex.lab = 1, line= 2)

axis(1, at = unique_AM_days_st, labels = c("32", "80", "116", "158"))
title(xlab = "Days", cex.lab = 1.25 ,line = 2.25)

letters(x = 5, y = 97, "b)", cex = 1.5)



##############################################################################################



par(mar  = c(4,5,1,1), bty = "l", new = FALSE)
plot(env_PCs[,3] ~ jitter(AM_days_st, 1),
     data = Exp_design_all_2, xaxt = "n", ylab = "", xlab = "", type = "n", xlim = c(min(unique_AM_days_st)*1.25,max(unique_AM_days_st)*1.25),  xaxs = "i")

polygon(x = c(new_data_days$AM_days_st[1:100], new_data_days$AM_days_st[100:1]),
        y = c(predicted_env_PC3_time$upper[1:100], predicted_env_PC3_time$lower[100:1]), col = transparent("blue", trans.val = 0.6), border = FALSE) 

points(env_PCs[,3] ~ jitter(AM_days_st, 0.5), pch = 21, col= "black",bg = transparent("blue", trans.val = 0.75), cex = 1.1, data = Exp_design_all_2)

lines(x = new_data_days$AM_days_st,y = predicted_env_PC3_time$fit, col = "black", lwd = 2)

title(ylab = "Environment PC3", cex.lab = 1, line= 3)
title(ylab = "(mostly dissolved oxygen)", cex.lab = 1, line= 2)

axis(1, at = unique_AM_days_st, labels = c("32", "80", "116", "158"))
title(xlab = "Days", cex.lab = 1.25 ,line = 2.25)

letters(x = 5, y = 97, "c)", cex = 1.5)
```


#### Environmental parameters VS community variability


```{r,   fig.width = 6, fig.height = 3, dpi = 600, dev.args= list(pointsize=8)}
set.seed(1)
#svg(file = "plots/Community structure analysis/beta_dataiation.svg", width = 6, height = 3, pointsize = 8)

par(mfrow = c(1,2))

par(mar  = c(4,4,1,1), bty = "l", new = FALSE)
plot(beta_data$observed_distances ~ resid_PC3,
     data = Exp_design_all_2, xaxt = "n", ylab = "", xlab = "", type = "n")

polygon(x = c(new_data_obs_PC3$resid_PC3[1:100], new_data_obs_PC3$resid_PC3[100:1]),
        y = c(predicted_obs_PC3$upper[1:100], predicted_obs_PC3$lower[100:1]), col = transparent("grey20", trans.val = 0.6), border = FALSE) 

points(beta_data$observed_distances[Exp_design_all_2$AM == 1] ~ resid_PC3, pch = 21, col= "black",bg = transparent("grey80", trans.val = 0.6), cex = 1.1, data = Exp_design_all_2[Exp_design_all_2$AM == 1,])

points(beta_data$observed_distances[Exp_design_all_2$AM == 2] ~ resid_PC3, pch = 21, col= "black",bg = transparent("grey50", trans.val = 0.6), cex = 1.1, data = Exp_design_all_2[Exp_design_all_2$AM == 2,])

points(beta_data$observed_distances[Exp_design_all_2$AM == 3] ~ resid_PC3, pch = 21, col= "black",bg = transparent("grey20", trans.val = 0.6), cex = 1.1, data = Exp_design_all_2[Exp_design_all_2$AM == 3,])

points(beta_data$observed_distances[Exp_design_all_2$AM == 4] ~ resid_PC3, pch = 21, col= "black",bg = transparent("black", trans.val = 0.6), cex = 1.1, data = Exp_design_all_2[Exp_design_all_2$AM == 4,])

lines(x = new_data_obs_PC3$resid_PC3,y = predicted_obs_PC3$fit, col = "black", lwd = 2, lty = 2)


title(ylab = "Observed community variability", cex.lab = 1.25, line= 2.25)
axis(1)
title(xlab = "Residuals of environmental PC3", cex.lab = 1 ,line = 2)
title(xlab = "(Dissolved oxygen without temporal effects)", cex.lab = 0.9 ,line = 3)


letters(x = 5, y = 97, "a)", cex = 1.5)

#####################################################################################################################


par(mar  = c(4,4,1,1), bty = "l", new = FALSE)
plot(beta_data$deviation_distances ~ resid_PC3,
     data = Exp_design_all_2, xaxt = "n", ylab = "", xlab = "", type = "n")

polygon(x = c(new_data_obs_PC3$resid_PC3[1:100], new_data_obs_PC3$resid_PC3[100:1]),
        y = c(predicted_dev_PC3$upper[1:100], predicted_dev_PC3$lower[100:1]), col = transparent("grey20", trans.val = 0.6), border = FALSE) 

points(beta_data$deviation_distances[Exp_design_all_2$AM == 1] ~ resid_PC3, pch = 21, col= "black",bg = transparent("grey80", trans.val = 0.6), cex = 1.1, data = Exp_design_all_2[Exp_design_all_2$AM == 1,])

points(beta_data$deviation_distances[Exp_design_all_2$AM == 2] ~ resid_PC3, pch = 21, col= "black",bg = transparent("grey50", trans.val = 0.6), cex = 1.1, data = Exp_design_all_2[Exp_design_all_2$AM == 2,])

points(beta_data$deviation_distances[Exp_design_all_2$AM == 3] ~ resid_PC3, pch = 21, col= "black",bg = transparent("grey20", trans.val = 0.6), cex = 1.1, data = Exp_design_all_2[Exp_design_all_2$AM == 3,])

points(beta_data$deviation_distances[Exp_design_all_2$AM == 4] ~ resid_PC3, pch = 21, col= "black",bg = transparent("black", trans.val = 0.6), cex = 1.1, data = Exp_design_all_2[Exp_design_all_2$AM == 4,])

lines(x = new_data_obs_PC3$resid_PC3,y = predicted_dev_PC3$fit, col = "black", lwd = 2, lty = 2)


title(ylab = "Beta deviation", cex.lab = 1.25, line= 2.25)
axis(1)
title(xlab = "Residuals of environmental PC3", cex.lab = 1 ,line = 2)
title(xlab = "(Dissolved oxygen without temporal effects)", cex.lab = 0.9 ,line = 3)

par(new = TRUE, mar = c(0,0,0,0), bty = "n")
plot(NA, ylim = c(0,100), xlim = c(0,100), xaxt = "n", yaxt = "n")

legend(legend = c("32 days",
                  "80 days",
                  "116 days",
                  "158 days"), x = 100, y = 100, bty = "n", pch = 21, col = "black", pt.bg = c(transparent("grey80", trans.val = 0.6),
                                                                                              transparent("grey50", trans.val = 0.6),
                                                                                              transparent("grey20", trans.val = 0.6),
                                                                                              transparent("black", trans.val = 0.6)), xjust = 1, yjust = 1)

letters(x = 5, y = 97, "b)", cex = 1.5)
#dev.off()
```


