---
title: "Variation partitioning  with previous community"
author: "Rodolfo Pelinson"
date: "2025-10-17"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, warning=FALSE, echo = FALSE, include=FALSE}
dir<-("C:/Users/rodol/OneDrive/repos/PrioEff_TimeOfAssembly")
```

```{r}
source(paste(sep = "/",dir,"functions/remove_sp.R"))
source(paste(sep = "/",dir,"functions/varpart_manyglm.R"))
source(paste(sep = "/",dir,"functions/R2_manyglm.R"))
source(paste(sep = "/",dir,"functions/letters.R"))
```

```{r, message = FALSE, warning = FALSE}
library(vegan)
library(gllvm)
library(mvabund)
```

```{r,  warning=FALSE, message = FALSE}
source(paste(sep = "/",dir,"ajeitando_planilhas.R"))
```

Building the community matrix with one step in time delayed (the predictor community)

```{r}
#Excluding the first survey
comm_all_2 <- comm_all[Exp_design_all$AM != 1,]
Exp_design_all_2 <- Exp_design_all[Exp_design_all$AM != 1,]

#Making a prior occupancy predictor
comm_all_prior <- comm_all[Exp_design_all$AM != 4,]
Exp_design_all_prior <- Exp_design_all[Exp_design_all$AM != 4,]

#Now excluding the late treatment because it complicate things
comm_all_2 <- comm_all_2[Exp_design_all_2$treatments != "atrasado",]
comm_all_prior <- comm_all_prior[Exp_design_all_prior$treatments != "atrasado",]
Env_new <- Env_2_4[Exp_design_all_2$treatments != "atrasado",-c(1)]
Exp_design_all_2 <- Exp_design_all_2[Exp_design_all_2$treatments != "atrasado",]
Exp_design_all_prior <- Exp_design_all_prior[Exp_design_all_prior$treatments != "atrasado",]


ncol(comm_all_2)
ncol(comm_all_prior)

comm_all_2 <- remove_sp(comm_all_2, 4)
comm_all_prior <- remove_sp(comm_all_prior, 10)

ncol(comm_all_2)
ncol(comm_all_prior)

nrow(comm_all_2)
nrow(comm_all_prior)
nrow(Env_new)
nrow(Exp_design_all_2)
```

To reduce dimensionality of data and standardize as much as possible the number of predictors in each set of predictors we ran a nmds on the prior community state matrix and a PCA on the environmental predictors

```{r, message = FALSE}
ID <-  as.factor(Exp_design_all_2$sites)
block <-  data.frame(block2 = Exp_design_all_2$block2)

Env_st <- decostand(Env_new, method = "stand")
pca_env <- rda(Env_st)
sum(c(pca_env$CA$eig/sum(pca_env$CA$eig))[1:3])
Env_st_pca <- data.frame(pca_env$CA$u[,1:3])

pca_env$CA$v

comm_all_prior_total <- data.frame(decostand(comm_all_prior, method = "total", MARGIN = 2))
set.seed(1); nmds_prior <- metaMDS(comm_all_prior_total, distance  = "bray", k = 3, try = 100, trymax = 100)
comm_all_prior_nmds <- data.frame(nmds_prior$points)
comm_all_prior_nmds <- decostand(comm_all_prior_nmds, method = "stand")

AM <- data.frame(AM = as.numeric(Exp_design_all_2$AM))
AM <- decostand(AM, method = "stand")
AM$AM_quad <- AM$AM^2


predictors <- list(block = block,
                   Env = Env_st_pca,
                   Time = AM,
                   Priority = comm_all_prior_nmds)

lapply(predictors, FUN = nrow)
lapply(predictors, FUN = ncol)


```

We ended up with this number of predictors:

Prior community structure: 3
Time: 2
Environment: 3
Block: 1 factor with 3 levels (effectively 2 predictors)

Variation partitioning

```{r}
varpart_priority <- varpart_manyglm(comm_all_2, pred = predictors, DF_adj_r2 = FALSE)

varpart_priority$R2_fractions_com

total_r2 <- varpart_priority$R2_models$`block-Env-Time-Priority`
total_r2
```

Scaling fractions so the added partial ones won't larger than the total R² of the model (which may sometime happen).

```{r}



##### PLOT
full_model_sp <- varpart_priority$R2_models_sp$block.Env.Time.Priority
names(full_model_sp) <- rownames(varpart_priority$R2_models_sp)
ord_sp <- order(full_model_sp, decreasing = TRUE)

full_model_sp<- full_model_sp[ord_sp]


full_block <-  varpart_priority$R2_fractions_sp$R2_full_fraction$block
names(full_block) <- rownames(varpart_priority$R2_fractions_sp$R2_full_fraction)

full_Env <-  varpart_priority$R2_fractions_sp$R2_full_fraction$Env
names(full_Env) <- rownames(varpart_priority$R2_fractions_sp$R2_full_fraction)

full_Time <-  varpart_priority$R2_fractions_sp$R2_full_fraction$Time
names(full_Time) <- rownames(varpart_priority$R2_fractions_sp$R2_full_fraction)

full_Priority <-  varpart_priority$R2_fractions_sp$R2_full_fraction$Priority
names(full_Priority) <- rownames(varpart_priority$R2_fractions_sp$R2_full_fraction)


pure_block <-  varpart_priority$R2_fractions_sp$R2_pure_fraction$block
names(pure_block) <- rownames(varpart_priority$R2_fractions_sp$R2_pure_fraction)

pure_Env <-  varpart_priority$R2_fractions_sp$R2_pure_fraction$Env
names(pure_Env) <- rownames(varpart_priority$R2_fractions_sp$R2_pure_fraction)

pure_Time <-  varpart_priority$R2_fractions_sp$R2_pure_fraction$Time
names(pure_Time) <- rownames(varpart_priority$R2_fractions_sp$R2_pure_fraction)

pure_Priority <-  varpart_priority$R2_fractions_sp$R2_pure_fraction$Priority
names(pure_Priority) <- rownames(varpart_priority$R2_fractions_sp$R2_pure_fraction)

full_block <- full_block[ord_sp]
full_Env <- full_Env[ord_sp]
full_Time <- full_Time[ord_sp]
full_Priority <- full_Priority[ord_sp]

pure_block <- pure_block[ord_sp]
pure_Env <- pure_Env[ord_sp]
pure_Time <- pure_Time[ord_sp]
pure_Priority <- pure_Priority[ord_sp]

shared_priority_others <- full_Priority - pure_Priority


pure_block[pure_block < 0] <- 0
pure_Env[pure_Env < 0] <- 0
pure_Time[pure_Time < 0] <- 0
pure_Priority[pure_Priority < 0] <- 0


pure_frac_summed <- pure_block + pure_Env + pure_Time + pure_Priority

scale <- full_model_sp/pure_frac_summed

scale[scale > 1] <- 1

pure_frac_summed_scaled <- pure_frac_summed * scale

cbind(pure_frac_summed_scaled, full_model_sp)

pure_block_scaled  <- pure_block * scale
pure_Env_scaled  <- pure_Env * scale
pure_Time_scaled  <- pure_Time * scale
pure_Priority_scaled  <- pure_Priority * scale


scale_shared <- (full_model_sp - pure_frac_summed)  / shared_priority_others
scale_shared[scale_shared > 1] <- 1

shared_priority_others[shared_priority_others < 0] <- 0

shared_priority_others_scaled <- shared_priority_others * scale_shared
```

Plot including shared effects between priority effects and others/

```{r,   fig.width = 6, fig.height = 5, dpi = 600, dev.args= list(pointsize=9)}

at_generator <- function(first, spacing, n){
  axis <- first
  for(i in 2:(n)){
    axis[i] <- first + spacing*(i-1)
  }
  return(axis)
}


#svg(file = "C:/Users/rodol/OneDrive/repos/PrioEff_TimeOfAssembly/Plots/Community structure analysis/varpart_reduced_dim.svg", width = 6, height = 5, pointsize = 9)
close.screen(all.screens = TRUE)
split.screen(matrix(c(0,0.3,0.625,1,
                      0.3,1,0.625,1,
                      0,0.3,0.25,0.625,
                      0.3,1,0.25,0.625), ncol = 4, nrow = 4, byrow = TRUE))

screen(4)
par(mar = c(2,1,1.5,1), xpd = NA)
barplot(full_model_sp, ylim = c(0,0.7), las = 2, border = "white", col = "#C7C7C7", xaxt = "n", xaxs = "i", width = 1, space = 0.5, xlim = c(0,20), yaxt = "n", ylab = "", xlab = "")
par(new = TRUE)
pure_scaleds <- rbind(pure_block_scaled, pure_Env_scaled, pure_Time_scaled, pure_Priority_scaled, shared_priority_others_scaled)
barplot(pure_scaleds, ylim = c(0,0.7), las = 2, col = c("#98DF8A", "#9EDAE5", "#FFBB78", "#F7B6D2", "#C5B0D5"), border = "white", xaxt = "n", xaxs = "i", width = 1, space = 0.5, xlim = c(0,20), yaxt = "n")
box(bty = "l")
names <- colnames(pure_scaleds)
names <- gsub("\\."," ", names)
font <- rep(3, length(names))
font[names == "Chironominae" | names == "Tanypodinae"] <- 1

names1 <- names
names3 <- names

names1[names == "Chironominae" | names == "Tanypodinae"] <- ""
names3[names != "Chironominae" & names != "Tanypodinae"] <- ""


axis(1, at = at_generator(first = 1, spacing = 1.5, n = length(names)), gap.axis = -10, tick = TRUE, labels = FALSE, las = 2, font = 3, line = 0)

axis(1, at = at_generator(first = 1, spacing = 1.5, n = length(names1)), gap.axis = -10, tick = FALSE, labels = names1, las = 2, font = 3, line = 0)
axis(1, at = at_generator(first = 1, spacing = 1.5, n = length(names3)), gap.axis = -10, tick = FALSE, labels = names3, las = 2, font = 1, line = 0)


axis(2, las = 2, line = 0, labels = FALSE)
letters(x = -2, y = 95, "d)", cex = 1.5)


#par(new = TRUE, mar = c(0,0,0,0), bty = "n")
#plot(NA, xlim = c(0,100), ylim = c(0,100), xaxt = "n", yaxt = "n", xaxs = "i", yaxs = "i", )




screen(3, new = FALSE)
par(mar = c(2,4,1.5,1), xpd = NA)
barplot(total_r2, ylim = c(0,0.7), las = 2, border = "white", col = "#C7C7C7", xaxt = "n", xaxs = "i", width = 1, space = 0.5, xlim = c(0,2), yaxt = "n", ylab = "", xlab = "")
par(new = TRUE)

shared_priority_com <- varpart_priority$R2_fractions_com[4,1] - varpart_priority$R2_fractions_com[4,2]
pure_scaleds <- as.matrix(c(varpart_priority$R2_fractions_com$R2_pure_fraction, shared_priority_com))

barplot(pure_scaleds, ylim = c(0,0.7), las = 2, col = c("#98DF8A", "#9EDAE5", "#FFBB78", "#F7B6D2", "#C5B0D5"), border = "white", xaxt = "n", xaxs = "i", width = 1, space = 0.5, xlim = c(0,2), yaxt = "n")
box(bty = "l")
#title(ylab = "Likelihood ratio R²", cex.lab = 1.25)

axis(1, at = c(1), gap.axis = -10, tick = FALSE, labels = "Community", las = 1, font = 1, line = -0.5)

title(ylab = "Likelihood ratio R²", cex.lab = 1.25)
axis(2, las = 2, line = 0)
letters(x = 5, y = 95, "c)", cex = 1.5)


screen(2, new = FALSE)
par(mar = c(2,1,1.5,1), xpd = NA)
pure_scaleds <- rbind(full_block, full_Env, full_Time, full_Priority)
barplot(pure_scaleds, ylim = c(0,0.7), las = 2, col = c("#98DF8A", "#9EDAE5", "#FFBB78", "#F7B6D2"), border = "transparent", xaxt = "n", xaxs = "i", width = 1, space = c(0,2), xlim = c(0,80), yaxt = "n", beside = TRUE, ylab = "", xlab = "")
box(bty = "l")
names <- colnames(pure_scaleds)
names <- gsub("\\."," ", names)
font <- rep(3, length(names))
font[names == "Chironominae" | names == "Tanypodinae"] <- 1

axis(1, at = at_generator(first = 4, spacing = 6, n = length(names)), gap.axis = -10, tick = TRUE, labels = FALSE, las = 2, font = 3, line = 0)
#axis(1, at = at_generator(first = 4, spacing = 6, n = length(c(names[1:8], c("",""),names[11:13]))), gap.axis = -10, tick = FALSE, labels = c(names[1:8], c("",""),names[11:13]), las = 2, font = 3, line = 0)
#axis(1, at = at_generator(first = 4, spacing = 6, n = length(c(rep("",8), names[9:10],rep("",3)))), gap.axis = -10, tick = FALSE, labels = c(rep("",8), names[9:10],rep("",3)), las = 2, font = 1, line = 0)
axis(2, las = 2, line = 0, labels = FALSE)

letters(x = -2, y = 95, "b)", cex = 1.5)


par(new = TRUE, mar = c(0,0,0,0), bty = "n")
plot(NA, xlim = c(0,100), ylim = c(0,100), xaxt = "n", yaxt = "n", xaxs = "i", yaxs = "i", ylab = "", xlab = "")

legend(x = 99, y = 99, xjust = 1, yjust = 1, fill = c("#98DF8A", "#9EDAE5", "#FFBB78","#F7B6D2", "#C5B0D5", "#C7C7C7"),
       legend = c("Block", "Water parameters", "Time", "Previous structure", "Shared with previous structure", "Shared among others"), border = "white", bty = "n")


screen(1, new = FALSE)
par(mar = c(2,4,1.5,1), xpd = NA)

pure_scaleds <- as.matrix(varpart_priority$R2_fractions_com$R2_full_fraction)

barplot(pure_scaleds, ylim = c(0,0.7), las = 2, col = c("#98DF8A", "#9EDAE5", "#FFBB78", "#F7B6D2", "#C5B0D5"), border = "white", xaxt = "n", xaxs = "i", width = 1, space = c(0,1), xlim = c(0,6), yaxt = "n", beside = TRUE, ylab = "", xlab = "")
box(bty = "l")
#axis(1, at = c(3), gap.axis = -10, tick = FALSE, labels = "Community", las = 1, font = 1, line = -0.5)
#title(ylab = "Likelihood ratio R²", cex.lab = 1.25)

#axis(1, at = c(3), gap.axis = -10, tick = FALSE, labels = "Community", las = 1, font = 1, line = -0.5)


title(ylab = "Likelihood ratio R²", cex.lab = 1.25)
axis(2, las = 2, line = 0)
letters(x = 5, y = 95, "a)", cex = 1.5)


#dev.off()
######


```

Now testing the significance of these fractions

```{r, cache = TRUE}
set.seed(3)
control <- permute::how(within = permute::Within(type = 'free'),
                        plots = Plots(strata = ID, type = 'free'),
                        nperm = 999)
permutations <- shuffleSet(nrow(comm_all_2), control = control)


anova_block_pure <- anova(varpart_priority$models$`block-Env-Time-Priority`, varpart_priority$models$`Env-Time-Priority`, show.time = "all", resamp = "pit.trap", bootID = permutations)
anova_block_pure

anova_Env_pure <- anova(varpart_priority$models$`block-Env-Time-Priority`, varpart_priority$models$`block-Time-Priority`, show.time = "all", resamp = "pit.trap", bootID = permutations)
anova_Env_pure

anova_Time_pure <- anova(varpart_priority$models$`block-Env-Time-Priority`, varpart_priority$models$`block-Env-Priority`, show.time = "all", resamp = "pit.trap", bootID = permutations)
anova_Time_pure

anova_Priority_pure <- anova(varpart_priority$models$`block-Env-Time-Priority`, varpart_priority$models$`block-Env-Time`, show.time = "all", resamp = "pit.trap", bootID = permutations)
anova_Priority_pure

anova_block <- anova(varpart_priority$models$block, varpart_priority$model_null, show.time = "all", resamp = "pit.trap", bootID = permutations)
anova_block

anova_Env <- anova(varpart_priority$models$Env, varpart_priority$model_null, show.time = "all", resamp = "pit.trap", bootID = permutations)
anova_Env

anova_Time <- anova(varpart_priority$models$Time, varpart_priority$model_null, show.time = "all", resamp = "pit.trap", bootID = permutations)
anova_Time

anova_Priority <- anova(varpart_priority$models$Priority, varpart_priority$model_null, show.time = "all", resamp = "pit.trap", bootID = permutations)
anova_Priority

```
